---
title: "PRISM linear mixed regression"
author: "Yi"
date: "5/18/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(tidyverse)
library(lme4)
library(stargazer)
library(pander)
library(sjPlot)
```


```{r, include=FALSE}
data <- read.csv("/Users/zhan039/Desktop/USC_HEAL/PRISM/05182020/PRISMCompleters_w_Menthol_Status_24Apr2020.csv", na.strings = c("", "."))
```

## Explore the data
```{r, echo=FALSE}
rat.time <- select(data, sid,  smoking_condition_check, patch_condition, blinding_condn, rat_delay_time, menthol_status)
rat.time$rat_delay_time <- as.numeric(rat.time$rat_delay_time)
# head(rat.time)


ggplot(data = rat.time, aes(x = rat_delay_time, group = as.factor(blinding_condn), fill = as.factor(blinding_condn))) + 
  geom_histogram( position = "dodge") +
  scale_fill_discrete(name = "Blind Condition", 
                      breaks = c(1, 2, 3, 4),
                      labels = c("no smoking + placebo patch", "no smoking + active patch", "smoking + placebo patch", "smoking + active patch")) +
  xlab("Rat Delay Time") +
  ylab("Frequency") +
  ggtitle("Distribution of Rat Delay Time across Blind Conditions") +
  theme(legend.position = "bottom", legend.direction = "vertical", plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "inches")) +
  guides(fill = guide_legend(ncol = 2, nrow = 2, byrow = TRUE))

  

ggplot(data = rat.time, aes(x = as.factor(smoking_condition_check), y = rat_delay_time, fill = as.factor(patch_condition))) + 
         geom_boxplot() +
  scale_fill_discrete(name = "Patch Condition",
                      breaks = c(0, 1),
                      labels = c("Placebo", "Active")) +
  xlab("Smoking Condition") +
  scale_x_discrete(breaks = c(0:1), labels = c("No Smoking", "Smoking")) +
  ylab("Rat Delay Time") +
  ggtitle("Distribution of Rat Delay Time across Smoking Condition and Patch Condition")

```

## Model 1: Main Effects Smoking and Patch Only
```{r, echo=FALSE}
a <- lmer(rat_delay_time ~ smoking_condition_check + patch_condition + (1|sid), data = rat.time)
summary(a)

pander(anova(a))

# stargazer(a, type = "latex", notes = "stargazer latex")




# b <- lme(rat_delay_time ~ smoking_condition_check + patch_condition, data = rat.time, random = ~ 1|sid)
# summary(a)
# summary(b)
# anova(b)
# qqnorm(resid(b))
# qqline(resid(b))
```

\begin{table}[!htbp] \centering 
  \caption{} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{1}{c}{\textit{Dependent variable:}} \\ 
\cline{2-2} 
\\[-1.8ex] & rat\_delay\_time \\ 
\hline \\[-1.8ex] 
 smoking\_condition\_check & 5.432$^{***}$ \\ 
  & (1.837) \\ 
  & \\ 
 patch\_condition & 4.023$^{**}$ \\ 
  & (1.837) \\ 
  & \\ 
 Constant & 29.625$^{***}$ \\ 
  & (2.590) \\ 
  & \\ 
\hline \\[-1.8ex] 
Observations & 264 \\ 
Log Likelihood & $-$1,140.744 \\ 
Akaike Inf. Crit. & 2,291.488 \\ 
Bayesian Inf. Crit. & 2,309.368 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{1}{r}{stargazer latex} \\ 
\end{tabular} 
\end{table} 

### Check residuals
```{r, echo=FALSE}

qqnorm(resid(a))
```

