---
title: "Linear Regression"
author: "Yi"
date: "5/31/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(tidyverse)
library(lm.beta)
library(psy)
library(effsize)
library(car)
```

```{r}
data <- read_sav("/Users/zhan039/Desktop/USC_HEAL/Menthol/fix_grow_data.sav")

data <- filter(data, piq_5 == 0 & PIQ_6c_T == 1 | piq_5 == 0 & piq_6___3 == 1)
```

## Table 3. Association of Menthol Status with Tobacco Deprivation-Induced Changes in Tobacco Withdrawal Outcomes
```{r}
# independent variables
table(data$shq_8, useNA = "ifany")  # menthol
data <- mutate(data, menthol = ifelse(shq_8 == 2, 0, shq_8)) # recode shq_8 as 0 and 1
table(data$menthol, useNA = "ifany") 

summary(data$ND_WSWS_Craving_Mean)
summary(data$ND_QSU_Factor1_Mean)
summary(data$ND_QSU_Factor2_Mean)
summary(data$ND_POMS_NM_Mean)
summary(data$ND_WSWS_Anger_Mean)
summary(data$ND_POMS_Anger_Mean)
summary(data$ND_WSWS_Anxiety_Mean)
summary(data$ND_POMS_Anxiety_Mean)
summary(data$ND_WSWS_Sadness_Mean)
summary(data$ND_POMS_Depression_Mean)
summary(data$ND_POMS_PM_Mean)
summary(data$ND_SHAPS_RC_Mean)
summary(data$ND_POMS_Confusion_Mean)
summary(data$ND_WSWS_Concentration_Mean)
summary(data$ND_CIS_Mean)
summary(data$ND_WSWS_Hunger_Mean)

# dependent variables
summary(data$DIFF_WSWS_Craving_Mean) 
summary(data$DIFF_QSU_Factor1_Mean)
summary(data$DIFF_QSU_Factor2_Mean)
summary(data$DIFF_POMS_NM_Mean)
summary(data$DIFF_WSWS_Anger_Mean)
summary(data$DIFF_POMS_Anger_Mean)
summary(data$DIFF_WSWS_Anxiety_Mean)
summary(data$DIFF_POMS_Anxiety_Mean)
summary(data$DIFF_WSWS_Sadness_Mean)
summary(data$DIFF_POMS_Depression_Mean)
summary(data$DIFF_POMS_PM_Mean)
summary(data$DIFF_SHAPS_RC_Mean)
summary(data$DIFF_POMS_Confusion_Mean)
summary(data$DIFF_WSWS_Concentration_Mean)
summary(data$DIFF_CIS_Mean)
summary(data$DIFF_WSWS_Hunger_Mean)

# Adjusted for:
table(data$piq_1, useNA = "ifany")  # gender (identity)
table(data$piq_2, useNA = "ifany")  # age
table(data$piq_7, useNA = "ifany")  # education
data <- mutate(data, education = ifelse(piq_7 == 1 | piq_7 == 2, 0, 1)) # recode piq_7 as 0 and 1
table(data$education, useNA = "ifany")
table(data$FTND_SUM, useNA = "ifany")  # FTND classification

```

## Main Effect Regressions: Menthal Status --> Study Outcomes - UNADJUSTED
### Smoking Motivation Regression
```{r}
lr1 <- lm(DIFF_WSWS_Craving_Mean ~ menthol + ND_WSWS_Craving_Mean, data = data)
lr1.std <- lm.beta(lr1)
summary(lr1.std)
confint(lr1.std)
```

```{r}
lr2 <- lm(DIFF_QSU_Factor1_Mean ~ menthol + ND_QSU_Factor1_Mean, data)
lr2.std <- lm.beta(lr2)
summary(lr2.std)
confint(lr2.std)
```

```{r}
lr3 <- lm(DIFF_QSU_Factor2_Mean ~ menthol + ND_QSU_Factor2_Mean, data)
lr3.std <- lm.beta(lr3)
summary(lr3.std)
confint(lr3.std)
```

### NA Regressions
```{r}
lr4 <- lm(DIFF_POMS_NM_Mean ~ menthol + ND_POMS_NM_Mean, data)
lr4.std <- lm.beta(lr4)
summary(lr4.std)
confint(lr4.std)
```

```{r}
lr5 <- lm(DIFF_WSWS_Anger_Mean ~ menthol + ND_WSWS_Anger_Mean, data)
lr5.std <- lm.beta(lr5)
summary(lr5.std)
confint(lr5.std)
```

```{r}
lr6 <- lm(DIFF_POMS_Anger_Mean ~ menthol + ND_POMS_Anger_Mean, data)
lr6.std <- lm.beta(lr6)
summary(lr6.std)
confint(lr6.std)
```

```{r}
lr7 <- lm(DIFF_WSWS_Anxiety_Mean ~ menthol + ND_WSWS_Anxiety_Mean, data)
lr7.std <- lm.beta(lr7)
summary(lr7.std)
confint(lr7.std)
```

```{r}
lr8 <- lm(DIFF_POMS_Anxiety_Mean ~ menthol + ND_POMS_Anxiety_Mean, data)
lr8.std <- lm.beta(lr8)
summary(lr8.std)
confint(lr8.std)
```

```{r}
lr9 <- lm(DIFF_WSWS_Sadness_Mean ~ menthol + ND_WSWS_Sadness_Mean, data)
lr9.std <- lm.beta(lr9)
summary(lr9.std)
confint(lr9.std)
```

```{r}
lr10 <- lm(DIFF_POMS_Depression_Mean ~ menthol + ND_POMS_Depression_Mean, data)
lr10.std <- lm.beta(lr10)
summary(lr10.std)
confint(lr10.std)
```

### Low PA Regressions
```{r}
lr11 <- lm(DIFF_POMS_PM_Mean ~ menthol + ND_POMS_PM_Mean, data)
lr11.std <- lm.beta(lr11)
summary(lr11.std)
confint(lr11.std)
```

```{r}
lr12 <- lm(DIFF_SHAPS_RC_Mean ~ menthol + ND_SHAPS_RC_Mean, data)
lr12.std <- lm.beta(lr12)
summary(lr12.std)
confint(lr12.std)
```

### Cognitive Regressions
```{r}
lr13 <- lm(DIFF_POMS_Confusion_Mean ~ menthol + ND_POMS_Confusion_Mean, data)
lr13.std <- lm.beta(lr13)
summary(lr13.std)
confint(lr13.std)
```

```{r}
lr14 <- lm(DIFF_WSWS_Concentration_Mean ~ menthol + ND_WSWS_Concentration_Mean, data)
lr14.std <- lm.beta(lr14)
summary(lr14.std)
confint(lr14.std)
```

```{r}
lr15 <- lm(DIFF_CIS_Mean ~ menthol + ND_CIS_Mean, data)
lr15.std <- lm.beta(lr15)
summary(lr15.std)
confint(lr15.std)
```

### Other Regressions
```{r}
lr16 <- lm(DIFF_WSWS_Hunger_Mean ~ menthol + ND_WSWS_Hunger_Mean, data)
lr16.std <- lm.beta(lr16)
summary(lr16.std)
confint(lr16.std)
```

## Main Effect Regressions menthol --> Study Outcomes -- Adjusted for age, gender, education, and FTND
### Smoking Motivation Regressions
```{r}
lr1.a <- lm(DIFF_WSWS_Craving_Mean ~ menthol + ND_WSWS_Craving_Mean + piq_1 + piq_2 + education + FTND_SUM, data = data)
lr1.a.std <- lm.beta(lr1.a)
summary(lr1.a.std)
confint(lr1.a.std)
```

```{r}
lr2.a <- lm(DIFF_QSU_Factor1_Mean ~ menthol + ND_QSU_Factor1_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr2.a.std <- lm.beta(lr2.a)
summary(lr2.a.std)
confint(lr2.a.std)
```

```{r}
lr3.a <- lm(DIFF_QSU_Factor2_Mean ~ menthol + ND_QSU_Factor2_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr3.a.std <- lm.beta(lr3.a)
summary(lr3.a.std)
confint(lr3.a.std)
```

### NA Regressions
```{r}
lr4.a <- lm(DIFF_POMS_NM_Mean ~ menthol + ND_POMS_NM_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr4.a.std <- lm.beta(lr4.a)
summary(lr4.a.std)
confint(lr4.a.std)
```

```{r}
lr5.a <- lm(DIFF_WSWS_Anger_Mean ~ menthol + ND_WSWS_Anger_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr5.a.std <- lm.beta(lr5.a)
summary(lr5.a.std)
confint(lr5.a.std)
```

```{r}
lr6.a <- lm(DIFF_POMS_Anger_Mean ~ menthol + ND_POMS_Anger_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr6.a.std <- lm.beta(lr6.a)
summary(lr6.a.std)
confint(lr6.a.std)
```

```{r}
lr7.a <- lm(DIFF_WSWS_Anxiety_Mean ~ menthol + ND_WSWS_Anxiety_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr7.a.std <- lm.beta(lr7.a)
summary(lr7.a.std)
confint(lr7.a.std)
```

```{r}
lr8.a <- lm(DIFF_POMS_Anxiety_Mean ~ menthol + ND_POMS_Anxiety_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr8.a.std <- lm.beta(lr8.a)
summary(lr8.a.std)
confint(lr8.a.std)
```

```{r}
lr9.a <- lm(DIFF_WSWS_Sadness_Mean ~ menthol + ND_WSWS_Sadness_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr9.a.std <- lm.beta(lr9.a)
summary(lr9.a.std)
confint(lr9.a.std)
```

```{r}
lr10.a <- lm(DIFF_POMS_Depression_Mean ~ menthol + ND_POMS_Depression_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr10.a.std <- lm.beta(lr10.a)
summary(lr10.a.std)
confint(lr10.a.std)
```

### Low PA Regressions
```{r}
lr11.a <- lm(DIFF_POMS_PM_Mean ~ menthol + ND_POMS_PM_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr11.a.std <- lm.beta(lr11.a)
summary(lr11.a.std)
confint(lr11.a.std)
```

```{r}
lr12.a <- lm(DIFF_SHAPS_RC_Mean ~ menthol + ND_SHAPS_RC_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr12.a.std <- lm.beta(lr12.a)
summary(lr12.a.std)
confint(lr12.a.std)
```

### Cognitive Regression
```{r}
lr13.a <- lm(DIFF_POMS_Confusion_Mean ~ menthol + ND_POMS_Confusion_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr13.a.std <- lm.beta(lr13.a)
summary(lr13.a.std)
confint(lr13.a.std)
```

```{r}
lr14.a <- lm(DIFF_WSWS_Concentration_Mean ~ menthol + ND_WSWS_Concentration_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr14.a.std <- lm.beta(lr14.a)
summary(lr14.a.std)
confint(lr14.a.std)
```

```{r}
lr15.a <- lm(DIFF_CIS_Mean ~ menthol + ND_CIS_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr15.a.std <- lm.beta(lr15.a)
summary(lr15.a.std)
confint(lr15.a.std)
```

### Other Regressions
```{r}
lr16.a <- lm(DIFF_WSWS_Hunger_Mean ~ menthol + ND_WSWS_Hunger_Mean + piq_1 + piq_2 + education + FTND_SUM, data)
lr16.a.std <- lm.beta(lr16.a)
summary(lr16.a.std)
confint(lr16.a.std)
```

## Table 2. Deprivation Effects for Study Outcomes
```{r}
Mean.sd.n <- function(var){
    a <- cbind(mean(var, na.rm = T), 
               sd(var, na.rm = T),
               sum(!is.na(var)))
    rownames(a) <- attr(var, which = "label")
    colnames(a) <- c("Mean", "SD", "Valid N")
    return(a)
}

ValidN <- function(var){
  return(sum(!is.na(var)))
}

Ttest <- function(var){
  LeveneTest <- leveneTest(var, group = as.factor(filter.data$shq_8), center = mean)
  LeveneTest$result[1] <- ifelse(LeveneTest$`Pr(>F)`[1] < 0.05, FALSE, TRUE)
  LeveneTest$result[2] <- !LeveneTest$result[1]
  return(t.test(var[filter.data$shq_8 == 1], var[filter.data$shq_8 == 2], var.equal = LeveneTest$result[1]))
}

CohensD <- function(var) {
  d <- cohen.d(var[filter.data$shq_8 == 1], var[filter.data$shq_8 == 2], paired = F, na.rm = T, within = F, hedges.correction = F)
  return(d)
}

data$diff_co <- data$d_co - data$nd_co

varlist <- select(data, nd_co, d_co, diff_co, ND_WSWS_Craving_Mean, D_WSWS_Craving_Mean, DIFF_WSWS_Craving_Mean, ND_QSU_Factor1_Mean, D_QSU_Factor1_Mean, DIFF_QSU_Factor1_Mean, ND_QSU_Factor2_Mean, D_QSU_Factor2_Mean, DIFF_QSU_Factor2_Mean, ND_POMS_NM_Mean, D_POMS_NM_Mean, DIFF_POMS_NM_Mean, ND_WSWS_Anger_Mean, D_WSWS_Anger_Mean, DIFF_WSWS_Anger_Mean, ND_POMS_Anger_Mean, D_POMS_Anger_Mean, DIFF_POMS_Anger_Mean, ND_WSWS_Anxiety_Mean, D_WSWS_Anxiety_Mean, DIFF_WSWS_Anxiety_Mean, ND_POMS_Anxiety_Mean, D_POMS_Anxiety_Mean, DIFF_POMS_Anxiety_Mean, ND_WSWS_Sadness_Mean, D_WSWS_Sadness_Mean, DIFF_WSWS_Sadness_Mean, ND_POMS_Depression_Mean, D_POMS_Depression_Mean, DIFF_POMS_Depression_Mean, ND_POMS_PM_Mean, D_POMS_PM_Mean, DIFF_POMS_PM_Mean, ND_SHAPS_RC_Mean, D_SHAPS_RC_Mean, DIFF_SHAPS_RC_Mean, ND_POMS_Confusion_Mean, D_POMS_Confusion_Mean, DIFF_POMS_Confusion_Mean, ND_WSWS_Concentration_Mean, D_WSWS_Concentration_Mean, DIFF_WSWS_Concentration_Mean, ND_CIS_Mean, D_CIS_Mean, DIFF_CIS_Mean, ND_WSWS_Hunger_Mean, D_WSWS_Hunger_Mean, DIFF_WSWS_Hunger_Mean, shq_8)

# split data to menthol and unmenthol
filter.data <- varlist
table(filter.data$shq_8)
filter.data <- filter.data[!is.na(filter.data$shq_8), ]
menthol.data <- filter(filter.data, shq_8 == 1)
unmenthol.data <- filter(filter.data, shq_8 == 2)
nrow(menthol.data)
nrow(unmenthol.data)


# apply(varlist, 2, summary)
```

```{r sample of analysis}
# CO
Mean.sd.n(menthol.data$nd_co)
Mean.sd.n(menthol.data$d_co)
Mean.sd.n(menthol.data$diff_co)

Mean.sd.n(unmenthol.data$nd_co)
Mean.sd.n(unmenthol.data$d_co)
Mean.sd.n(unmenthol.data$diff_co)

select(menthol.data, d_co, nd_co, diff_co)
Ttest(filter.data$diff_co)
CohensD(filter.data$diff_co)
ValidN(filter.data$diff_co)

-35.355/sqrt(597)
# Urge/Craving
# WSWS craving
Mean.sd.n(menthol.data$ND_WSWS_Craving_Mean)
Mean.sd.n(menthol.data$D_WSWS_Craving_Mean)
Mean.sd.n(menthol.data$DIFF_WSWS_Craving_Mean)

Mean.sd.n(unmenthol.data$ND_WSWS_Craving_Mean)
Mean.sd.n(unmenthol.data$D_WSWS_Craving_Mean)
Mean.sd.n(unmenthol.data$DIFF_WSWS_Craving_Mean)

Ttest(filter.data$DIFF_WSWS_Craving_Mean)
CohensD(filter.data$DIFF_WSWS_Craving_Mean)
ValidN(filter.data$DIFF_WSWS_Craving_Mean)

cronbach(data[, c("nd_wsws_7", "nd_wsws_9", "nd_wsws_17", "nd_wsws_21")])
cronbach(data[, c("d_wsws_7", "d_wsws_9", "d_wsws_17", "d_wsws_21")])
```

```{r run all analyses}
# Mean SD N
apply(menthol.data[, -ncol(menthol.data)], 2, Mean.sd.n)
apply(unmenthol.data[, -ncol(unmenthol.data)], 2, Mean.sd.n)

diff_vars <- colnames(filter.data)[grepl("diff_", colnames(filter.data), ignore.case = T)]

apply(filter.data[, diff_vars], 2, CohensD)
apply(filter.data[, diff_vars], 2, Ttest)

```

```{r}
# Cronbach's alpha

# WSWS craving
cronbach(data[, c("nd_wsws_7", "nd_wsws_9", "nd_wsws_17", "nd_wsws_21")])
cronbach(data[, c("d_wsws_7", "d_wsws_9", "d_wsws_17", "d_wsws_21")])
t.test(data$D_WSWS_Craving_Mean, data$ND_WSWS_Craving_Mean, paired = T)
cohen.d(data$D_WSWS_Craving_Mean, data$ND_WSWS_Craving_Mean, paired = T, na.rm = T, within = F)
22.104/sqrt(589)
0.92063/1.0108
  
# QSU Factor 1
cronbach(data[, c("nd_qsu_1", "nd_qsu_3", "nd_qsu_6", "nd_qsu_7", "nd_qsu_10")])
cronbach(data[, c("d_qsu_1", "d_qsu_3", "d_qsu_6", "d_qsu_7", "d_qsu_10")])
t.test(data$D_QSU_Factor1_Mean, data$ND_QSU_Factor1_Mean, paired = T)
cohen.d(data$D_QSU_Factor1_Mean, data$ND_QSU_Factor1_Mean, paired = T, na.rm = T, within = F)
32.841/sqrt(588)

# QSU Factor 2
cronbach(data[, c("nd_qsu_2", "nd_qsu_4", "nd_qsu_5", "nd_qsu_8", "nd_qsu_9")])
cronbach(data[, c("d_qsu_2", "d_qsu_4", "d_qsu_5", "d_qsu_8", "d_qsu_9")])
t.test(data$D_QSU_Factor2_Mean, data$ND_QSU_Factor2_Mean, paired = T)
cohen.d(data$D_QSU_Factor2_Mean, data$ND_QSU_Factor2_Mean, paired = T, na.rm = T, within = F)
23.003/sqrt(591)

# POMS - Negative Mood
data <- mutate(data, nd_poms_38_reverse = 4 - nd_poms_38, nd_poms_66_reverse = 4 - nd_poms_66, d_poms_38_reverse = 4 - d_poms_38, d_poms_66_reverse = 4 - d_poms_66)

cronbach(data[, c("nd_poms_4", "nd_poms_14", "nd_poms_19", "nd_poms_24", "nd_poms_30", "nd_poms_33", "nd_poms_39", "nd_poms_42", "nd_poms_47", "nd_poms_53", "nd_poms_57", "nd_poms_71", "nd_poms_2", "nd_poms_11", "nd_poms_18", "nd_poms_66_reverse", "nd_poms_69", "nd_poms_43", "nd_poms_48", "nd_poms_60", "nd_poms_27", "nd_poms_7", "nd_poms_9", "nd_poms_21", "nd_poms_67", "nd_poms_38_reverse", "nd_poms_52", "nd_poms_58", "nd_poms_6", "nd_poms_10", "nd_poms_16", "nd_poms_22", "nd_poms_25", "nd_poms_29", "nd_poms_35", "nd_poms_36", "nd_poms_37", "nd_poms_45", "nd_poms_46", "nd_poms_49", "nd_poms_59", "nd_poms_62", "nd_poms_64", "nd_poms_5", "nd_poms_12", "nd_poms_20", "nd_poms_32", "nd_poms_68", "nd_poms_50", "nd_poms_65")])
cronbach(data[, c("d_poms_4", "d_poms_14", "d_poms_19", "d_poms_24", "d_poms_30", "d_poms_33", "d_poms_39", "d_poms_42", "d_poms_47", "d_poms_53", "d_poms_57", "d_poms_71", "d_poms_2", "d_poms_11", "d_poms_18", "d_poms_66_reverse", "d_poms_69", "d_poms_43", "d_poms_48", "d_poms_60", "d_poms_27", "d_poms_7", "d_poms_9", "d_poms_21", "d_poms_67", "d_poms_38_reverse", "d_poms_52", "d_poms_58", "d_poms_6", "d_poms_10", "d_poms_16", "d_poms_22", "d_poms_25", "d_poms_29", "d_poms_35", "d_poms_36", "d_poms_37", "d_poms_45", "d_poms_46", "d_poms_49", "d_poms_59", "d_poms_62", "d_poms_64", "d_poms_5", "d_poms_12", "d_poms_20", "d_poms_32", "d_poms_68", "d_poms_50", "d_poms_65")])
t.test(data$D_POMS_NM_Mean, data$ND_POMS_NM_Mean, paired = T)
cohen.d(data$D_POMS_NM_Mean, data$ND_POMS_NM_Mean, paired = T, na.rm = T, within = F)
6.5516/sqrt(588)

# WSWS Anger
cronbach(data[, c("nd_wsws_11", "nd_wsws_13", "nd_wsws_15")])
cronbach(data[, c("d_wsws_11", "d_wsws_13", "d_wsws_15")])
t.test(data$D_WSWS_Anger_Mean, data$ND_WSWS_Anger_Mean, paired = T)
cohen.d(data$D_WSWS_Anger_Mean, data$ND_WSWS_Anger_Mean, paired = T, na.rm = T, within = F)
13.764/sqrt(589)

# POMS Anger
cronbach(data[, c("nd_poms_4", "nd_poms_14", "nd_poms_19", "nd_poms_24", "nd_poms_30", "nd_poms_33", "nd_poms_39", "nd_poms_42", "nd_poms_47", "nd_poms_53", "nd_poms_57", "nd_poms_71")])
cronbach(data[, c("d_poms_4", "d_poms_14", "d_poms_19", "d_poms_24", "d_poms_30", "d_poms_33", "d_poms_39", "d_poms_42", "d_poms_47", "d_poms_53", "d_poms_57", "d_poms_71")])
t.test(data$D_POMS_Anger_Mean, data$ND_POMS_Anger_Mean, paired = T)
cohen.d(data$D_POMS_Anger_Mean, data$ND_POMS_Anger_Mean, paired = T, na.rm = T, within = F)
6.804/sqrt(588)

# WSWS Anxiety
data <- mutate(data, d_wsws_8_reverse = 4 - d_wsws_8, nd_wsws_8_reverse = 4 - nd_wsws_8)
cronbach(data[, c("nd_wsws_2", "nd_wsws_4", "nd_wsws_6", "nd_wsws_8_reverse")])
cronbach(data[, c("d_wsws_2", "d_wsws_4", "d_wsws_6", "d_wsws_8_reverse")])
t.test(data$D_WSWS_Anxiety_Mean, data$ND_WSWS_Anxiety_Mean, paired = T)
cohen.d(data$D_WSWS_Anxiety_Mean, data$ND_WSWS_Anxiety_Mean, paired = T, na.rm = T, within = F)
12.137/sqrt(588)


# POMS Anxiety
data <- mutate(data, d_poms_66_reverse = 4 - d_poms_66, nd_poms_66_reverse = 4 - nd_poms_66)
cronbach(data[, c("nd_poms_2", "nd_poms_11", "nd_poms_18", "nd_poms_66_reverse", "nd_poms_69", "nd_poms_43", "nd_poms_48", "nd_poms_60", "nd_poms_27")])
cronbach(data[, c("d_poms_2", "d_poms_11", "d_poms_18", "d_poms_66_reverse", "d_poms_69", "d_poms_43", "d_poms_48", "d_poms_60", "d_poms_27")])
t.test(data$D_POMS_Anxiety_Mean, data$ND_POMS_Anxiety_Mean, paired = T)
cohen.d(data$D_POMS_Anxiety_Mean, data$ND_POMS_Anxiety_Mean, paired = T, na.rm = T, within = F)
9.8165/sqrt(588)

# WSWS Sadness
data <- mutate(data, d_wsws_5_reverse = 4 - d_wsws_5, nd_wsws_5_reverse = 4 - nd_wsws_5, d_wsws_20_reverse = 4 - d_wsws_20, nd_wsws_20_reverse = 4 - nd_wsws_20)
cronbach(data[, c("nd_wsws_5_reverse", "nd_wsws_10", "nd_wsws_16", "nd_wsws_20_reverse")])
cronbach(data[, c("d_wsws_5_reverse", "d_wsws_10", "d_wsws_16", "d_wsws_20_reverse")])
t.test(data$D_WSWS_Sadness_Mean, data$ND_WSWS_Sadness_Mean, paired = T)
cohen.d(data$D_WSWS_Sadness_Mean, data$ND_WSWS_Sadness_Mean, paired = T, na.rm = T, within = F)
10.646/sqrt(589)

# POMS Depression
cronbach(data[, c("nd_poms_6", "nd_poms_10", "nd_poms_16", "nd_poms_22", "nd_poms_25", "nd_poms_29", "nd_poms_35", "nd_poms_36", "nd_poms_37", "nd_poms_45", "nd_poms_46", "nd_poms_49", "nd_poms_59", "nd_poms_62", "nd_poms_64")])
cronbach(data[, c("d_poms_6", "d_poms_10", "d_poms_16", "d_poms_22", "d_poms_25", "d_poms_29", "d_poms_35", "d_poms_36", "d_poms_37", "d_poms_45", "d_poms_46", "d_poms_49", "d_poms_59", "d_poms_62", "d_poms_64")])
t.test(data$D_POMS_Depression_Mean, data$ND_POMS_Depression_Mean, paired = T)
cohen.d(data$D_POMS_Depression_Mean, data$ND_POMS_Depression_Mean, paired = T, na.rm = T, within = F)
2.7458/sqrt(588)


# POMS positive mood
cronbach(data[, c("nd_poms_3", "nd_poms_13", "nd_poms_26", "nd_poms_40", "nd_poms_51", "nd_poms_72", "nd_poms_8", "nd_poms_17", "nd_poms_23", "nd_poms_31", "nd_poms_41", "nd_poms_54", "nd_poms_56", "nd_poms_61", "nd_poms_1", "nd_poms_15", "nd_poms_28", "nd_poms_34", "nd_poms_44", "nd_poms_55", "nd_poms_63", "nd_poms_70")])
cronbach(data[, c("d_poms_3", "d_poms_13", "d_poms_26", "d_poms_40", "d_poms_51", "d_poms_72", "d_poms_8", "d_poms_17", "d_poms_23", "d_poms_31", "d_poms_41", "d_poms_54", "d_poms_56", "d_poms_61", "d_poms_1", "d_poms_15", "d_poms_28", "d_poms_34", "d_poms_44", "d_poms_55", "d_poms_63", "d_poms_70")])
t.test(data$D_POMS_PM_Mean, data$ND_POMS_PM_Mean, paired = T)
cohen.d(data$D_POMS_PM_Mean, data$ND_POMS_PM_Mean, paired = T, na.rm = T, within = F)
-13.708/sqrt(586)


# SHAPS Anhedonia
data <- mutate(data, nd_shaps_1_reverse = 5 - nd_shaps_1, nd_shaps_2_reverse = 5 - nd_shaps_2, nd_shaps_3_reverse = 5 - nd_shaps_3, nd_shaps_4_reverse = 5 - nd_shaps_4, nd_shaps_5_reverse = 5 - nd_shaps_5, nd_shaps_6_reverse = 5 - nd_shaps_6, nd_shaps_7_reverse = 5 - nd_shaps_7, nd_shaps_8_reverse = 5 - nd_shaps_8, nd_shaps_9_reverse = 5 - nd_shaps_9, nd_shaps_10_reverse = 5 - nd_shaps_10, nd_shaps_11_reverse = 5 - nd_shaps_11, nd_shaps_12_reverse = 5 - nd_shaps_12, nd_shaps_13_reverse = 5 - nd_shaps_13, nd_shaps_14_reverse = 5 - nd_shaps_14, d_shaps_1_reverse = 5 - d_shaps_1, d_shaps_2_reverse = 5 - d_shaps_2, d_shaps_3_reverse = 5 - d_shaps_3, d_shaps_4_reverse = 5 - d_shaps_4, d_shaps_5_reverse = 5 - d_shaps_5, d_shaps_6_reverse = 5 - d_shaps_6, d_shaps_7_reverse = 5 - d_shaps_7, d_shaps_8_reverse = 5 - d_shaps_8, d_shaps_9_reverse = 5 - d_shaps_9, d_shaps_10_reverse = 5 - d_shaps_10, d_shaps_11_reverse = 5 - d_shaps_11, d_shaps_12_reverse = 5 - d_shaps_12, d_shaps_13_reverse = 5 - d_shaps_13, d_shaps_14_reverse = 5 - d_shaps_14)
cronbach(data[, c("nd_shaps_1_reverse", "nd_shaps_2_reverse", "nd_shaps_3_reverse", "nd_shaps_4_reverse", "nd_shaps_5_reverse", "nd_shaps_6_reverse", "nd_shaps_7_reverse", "nd_shaps_8_reverse", "nd_shaps_9_reverse", "nd_shaps_10_reverse", "nd_shaps_11_reverse", "nd_shaps_12_reverse", "nd_shaps_13_reverse", "nd_shaps_14_reverse")])
cronbach(data[, c("d_shaps_1_reverse", "d_shaps_2_reverse", "d_shaps_3_reverse", "d_shaps_4_reverse", "d_shaps_5_reverse", "d_shaps_6_reverse", "d_shaps_7_reverse", "d_shaps_8_reverse", "d_shaps_9_reverse", "d_shaps_10_reverse", "d_shaps_11_reverse", "d_shaps_12_reverse", "d_shaps_13_reverse", "d_shaps_14_reverse")])
t.test(data$D_SHAPS_RC_Mean, data$ND_SHAPS_RC_Mean, paired = T)
cohen.d(data$D_SHAPS_RC_Mean, data$ND_SHAPS_RC_Mean, paired = T, na.rm = T, within = F)
7.6028/sqrt(592)

# POMS Confusion
data <- mutate(data, d_poms_38_reverse = 4 - d_poms_38, nd_poms_38_reverse = 4 - nd_poms_38)
cronbach(data[, c("nd_poms_7", "nd_poms_9", "nd_poms_21", "nd_poms_67", "nd_poms_38_reverse", "nd_poms_52", "nd_poms_58")])
cronbach(data[, c("d_poms_7", "d_poms_9", "d_poms_21", "d_poms_67", "d_poms_38_reverse", "d_poms_52", "d_poms_58")])
t.test(data$D_POMS_Confusion_Mean, data$ND_POMS_Confusion_Mean, paired = T)
cohen.d(data$D_POMS_Confusion_Mean, data$ND_POMS_Confusion_Mean, paired = T, na.rm = T, within = F)
5.9006/sqrt(587)


# WSWS concentration
data <- mutate(data, d_wsws_3_reverse = 4 - d_wsws_3, nd_wsws_3_reverse = 4 - nd_wsws_3)
cronbach(data[, c("nd_wsws_3_reverse", "nd_wsws_19", "nd_wsws_22")])
cronbach(data[, c("d_wsws_3_reverse", "d_wsws_19", "d_wsws_22")])
t.test(data$D_WSWS_Concentration_Mean, data$ND_WSWS_Concentration_Mean, paired = T)
cohen.d(data$D_WSWS_Concentration_Mean, data$ND_WSWS_Concentration_Mean, paired = T, na.rm = T, within = F)
12.701/sqrt(589)


# CIS Impulsivity
data <- mutate(data, d_cis_4_reverse = 4 - d_cis_4, d_cis_5_reverse = 4 - d_cis_5, d_cis_6_reverse = 4 - d_cis_6, d_cis_8_reverse = 4 - d_cis_8, d_cis_10_reverse = 4 - d_cis_10, d_cis_12_reverse = 4 - d_cis_12, d_cis_15_reverse = 4 - d_cis_15, d_cis_18_reverse = 4 - d_cis_18, d_cis_19_reverse = 4 - d_cis_19, nd_cis_4_reverse = 4 - nd_cis_4, nd_cis_5_reverse = 4 - nd_cis_5, nd_cis_6_reverse = 4 - nd_cis_6, nd_cis_8_reverse = 4 - nd_cis_8, nd_cis_10_reverse = 4 - nd_cis_10, nd_cis_12_reverse = 4 - nd_cis_12, nd_cis_15_reverse = 4 - nd_cis_15, nd_cis_18_reverse = 4 - nd_cis_18, nd_cis_19_reverse = 4 - nd_cis_19)
cronbach(data[, c("nd_cis_1", "nd_cis_2", "nd_cis_3", "nd_cis_4_reverse", "nd_cis_5_reverse", "nd_cis_6_reverse", "nd_cis_7", "nd_cis_8_reverse", "nd_cis_9", 
  "nd_cis_10_reverse", "nd_cis_11", "nd_cis_12_reverse", "nd_cis_13", "nd_cis_14", "nd_cis_15_reverse", "nd_cis_16", "nd_cis_17", "nd_cis_18_reverse", "nd_cis_19_reverse")])
cronbach(data[, c("d_cis_1", "d_cis_2", "d_cis_3", "d_cis_4_reverse", "d_cis_5_reverse", "d_cis_6_reverse", "d_cis_7", "d_cis_8_reverse", "d_cis_9", 
  "d_cis_10_reverse", "d_cis_11", "d_cis_12_reverse", "d_cis_13", "d_cis_14", "d_cis_15_reverse", "d_cis_16", "d_cis_17", "d_cis_18_reverse", "d_cis_19_reverse")])
t.test(data$D_CIS_Mean, data$ND_CIS_Mean, paired = T)
cohen.d(data$D_CIS_Mean, data$ND_CIS_Mean, paired = T, na.rm = T, within = F)
11.436/sqrt(591)

# WSWS Hunger
data <- mutate(data, d_wsws_1_reverse = 4 - d_wsws_1, nd_wsws_1_reverse = 4 - nd_wsws_1)
cronbach(data[, c("nd_wsws_1_reverse", "nd_wsws_12", "nd_wsws_14", "nd_wsws_18", "nd_wsws_23")])
cronbach(data[, c("d_wsws_1_reverse", "d_wsws_12", "d_wsws_14", "d_wsws_18", "d_wsws_23")])
t.test(data$D_WSWS_Hunger_Mean, data$ND_WSWS_Hunger_Mean, paired = T)
cohen.d(data$D_WSWS_Hunger_Mean, data$ND_WSWS_Hunger_Mean, paired = T, na.rm = T, within = F)
9.325/sqrt(589)
```

