---
title: "Linear Regression"
author: "Yi"
date: "5/31/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(haven)
library(tidyverse)
library(ggplot2)
```

```{r}
data <- read_sav("/Users/zhan039/Desktop/USC_HEAL/GROW/GROW DATA-20190920T175512Z-001/GROW DATA/REDCap_wTeleform_Merged (scored + sorted)_06212018 (No 2nd survey) with DIFF.sav")
```

```{r}
# independent variables
table(data$shq_8, useNA = "ifany")  # menthol
data <- mutate(data, menthol = ifelse(shq_8 == 2, 0, shq_8)) # recode shq_8 as 0 and 1
table(data$menthol, useNA = "ifany") 

summary(data$ND_WSWS_Craving_Mean)
summary(data$ND_QSU_Factor1_Mean)
summary(data$ND_QSU_Factor2_Mean)
summary(data$ND_POMS_NM_Mean)
summary(data$ND_WSWS_Anger_Mean)
summary(data$ND_POMS_Anger_Mean)
summary(data$ND_WSWS_Anxiety_Mean)
summary(data$ND_POMS_Anxiety_Mean)
summary(data$ND_WSWS_Sadness_Mean)
summary(data$ND_POMS_Depression_Mean)
summary(data$ND_POMS_PM_Mean)
summary(data$ND_SHAPS_RC_Mean)
summary(data$ND_POMS_Confusion_Mean)
summary(data$ND_WSWS_Concentration_Mean)
summary(data$ND_CIS_Mean)
summary(data$ND_WSWS_Hunger_Mean)

# dependent variables
summary(data$DIFF_WSWS_Craving_Mean) 
summary(data$DIFF_QSU_Factor1_Mean)
summary(data$DIFF_QSU_Factor2_Mean)
summary(data$DIFF_POMS_NM_Mean)
summary(data$DIFF_WSWS_Anger_Mean)
summary(data$DIFF_POMS_Anger_Mean)
summary(data$DIFF_WSWS_Anxiety_Mean)
summary(data$DIFF_POMS_Anxiety_Mean)
summary(data$DIFF_WSWS_Sadness_Mean)
summary(data$DIFF_POMS_Depression_Mean)
summary(data$DIFF_POMS_PM_Mean)
summary(data$DIFF_SHAPS_RC_Mean)
summary(data$DIFF_POMS_Confusion_Mean)
summary(data$DIFF_WSWS_Concentration_Mean)
summary(data$DIFF_CIS_Mean)
summary(data$DIFF_WSWS_Hunger_Mean)

# Adjusted for:
table(data$piq_1, useNA = "ifany")  # gender (identity)
table(data$piq_2, useNA = "ifany")  # age
table(data$piq_7, useNA = "ifany")  # education
table(data$FTND_Classification, useNA = "ifany")  # FTND classification

```

## Main Effect Regressions: Menthal Status --> Study Outcomes - UNADJUSTED
### Smoking Motivation Regression
```{r}
lr1 <- lm(DIFF_WSWS_Craving_Mean ~ menthol + ND_WSWS_Craving_Mean, data = data)
summary(lr1)
```

```{r}
lr2 <- lm(DIFF_QSU_Factor1_Mean ~ menthol + ND_QSU_Factor1_Mean, data)
summary(lr2)
```

```{r}
lr3 <- lm(DIFF_QSU_Factor2_Mean ~ menthol + ND_QSU_Factor2_Mean, data)
summary(lr3)
```

### NA Regressions
```{r}
lr4 <- lm(DIFF_POMS_NM_Mean ~ menthol + ND_POMS_NM_Mean, data)
summary(lr4)
```

```{r}
lr5 <- lm(DIFF_WSWS_Anger_Mean ~ menthol + ND_WSWS_Anger_Mean, data)
summary(lr5)
```

```{r}
lr6 <- lm(DIFF_POMS_Anger_Mean ~ menthol + ND_POMS_Anger_Mean, data)
summary(lr6)
```

```{r}
lr7 <- lm(DIFF_WSWS_Anxiety_Mean ~ menthol + ND_WSWS_Anxiety_Mean, data)
summary(lr7)
```

```{r}
lr8 <- lm(DIFF_POMS_Anxiety_Mean ~ menthol + ND_POMS_Anxiety_Mean, data)
summary(lr8)
```

```{r}
lr9 <- lm(DIFF_WSWS_Sadness_Mean ~ menthol + ND_WSWS_Sadness_Mean, data)
summary(lr9)
```

```{r}
lr10 <- lm(DIFF_POMS_Depression_Mean ~ menthol + ND_POMS_Depression_Mean, data)
summary(lr10)
```

### Low PA Regressions
```{r}
lr11 <- lm(DIFF_POMS_PM_Mean ~ menthol + ND_POMS_PM_Mean, data)
summary(lr11)
```

```{r}
lr12 <- lm(DIFF_SHAPS_RC_Mean ~ menthol + ND_SHAPS_RC_Mean, data)
summary(lr12)
```

### Cognitive Regressions
```{r}
lr13 <- lm(DIFF_POMS_Confusion_Mean ~ menthol + ND_POMS_Confusion_Mean, data)
summary(lr13)
```

```{r}
lr14 <- lm(DIFF_WSWS_Concentration_Mean ~ menthol + ND_WSWS_Concentration_Mean, data)
summary(lr14)
```

```{r}
lr15 <- lm(DIFF_CIS_Mean ~ menthol + ND_CIS_Mean, data)
summary(lr15)
```

### Other Regressions
```{r}
lr16 <- lm(DIFF_WSWS_Hunger_Mean ~ menthol + ND_WSWS_Hunger_Mean, data)
summary(lr16)
```

## Main Effect Regressions menthol --> Study Outcomes -- Adjusted for age, gender, education, and FTND
### Smoking Motivation Regressions
```{r}
lr1.a <- lm(DIFF_WSWS_Craving_Mean ~ menthol + ND_WSWS_Craving_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data = data)
summary(lr1.a)
```

```{r}
lr2.a <- lm(DIFF_QSU_Factor1_Mean ~ menthol + ND_QSU_Factor1_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr2.a)
```

```{r}
lr3.a <- lm(DIFF_QSU_Factor2_Mean ~ menthol + ND_QSU_Factor2_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr3.a)
```

### NA Regressions
```{r}
lr4.a <- lm(DIFF_POMS_NM_Mean ~ menthol + ND_POMS_NM_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr4.a)
```

```{r}
lr5.a <- lm(DIFF_WSWS_Anger_Mean ~ menthol + ND_WSWS_Anger_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr5.a)
```

```{r}
lr6.a <- lm(DIFF_POMS_Anger_Mean ~ menthol + ND_POMS_Anger_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr6.a)
```

```{r}
lr7.a <- lm(DIFF_WSWS_Anxiety_Mean ~ menthol + ND_WSWS_Anxiety_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr7.a)
```

```{r}
lr8.a <- lm(DIFF_POMS_Anxiety_Mean ~ menthol + ND_POMS_Anxiety_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr8.a)
```

```{r}
lr9.a <- lm(DIFF_WSWS_Sadness_Mean ~ menthol + ND_WSWS_Sadness_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr9.a)
```

```{r}
lr10.a <- lm(DIFF_POMS_Depression_Mean ~ menthol + ND_POMS_Depression_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr10.a)
```

### Low PA Regressions
```{r}
lr11.a <- lm(DIFF_POMS_PM_Mean ~ menthol + ND_POMS_PM_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr11.a)
```

```{r}
lr12.a <- lm(DIFF_SHAPS_RC_Mean ~ menthol + ND_SHAPS_RC_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr12.a)
```

### Cognitive Regression
```{r}
lr13.a <- lm(DIFF_POMS_Confusion_Mean ~ menthol + ND_POMS_Confusion_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr13.a)
```

```{r}
lr14.a <- lm(DIFF_WSWS_Concentration_Mean ~ menthol + ND_WSWS_Concentration_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr14.a)
```

```{r}
lr15.a <- lm(DIFF_CIS_Mean ~ menthol + ND_CIS_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr15.a)
```

### Other Regressions
```{r}
lr16.a <- lm(DIFF_WSWS_Hunger_Mean ~ menthol + ND_WSWS_Hunger_Mean + piq_1 + piq_2 + piq_7 + FTND_Classification, data)
summary(lr16.a)
```

