---
title: "Repeated Responses of Remaining Variables"
author: "Yi"
date: "4/7/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
library(haven)
library(tidyverse)
```

# 0 mg 
```{r}
data <- read_sav("/Users/zhan039/Desktop/USC_HEAL/P4/03242020/0mg_with scoring added_3.23.2020.sav")
```

```{r}
Table.Print <- function(table, title) {
  if (nrow(table) > 0) {
    knitr::kable(table, caption = title)
  }
}
```

## MNWS_PreE_Mean MNWS_PostE_Mean MNWS_PostR_Mean
```{r}
# check whether all responses are the same
index.MNWS <- data %>% select(., MNWS_PreE_Mean, MNWS_PostE_Mean, MNWS_PostR_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
MNWS <- data[index.MNWS, c("redcap_id", "MNWS_PreE_Mean", "MNWS_PostE_Mean", "MNWS_PostR_Mean")]
MNWS_result <- MNWS %>% mutate(., SameValue = MNWS_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(MNWS_result, "MNWS")
```

There is/are `r nrow(MNWS_result)` participant(s) have the same value to MNWS_PreE_Mean, MNWS_PostE_Mean, and MNWS_PostR_Mean.

## QSU_PreE_Mean QSU_PostE_Mean QSU_PostR_Mean 
```{r}
index.QSU <- data %>% select(., QSU_PreE_Mean, QSU_PostE_Mean, QSU_PostR_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
QSU <- data[index.QSU, c("redcap_id", "QSU_PreE_Mean", "QSU_PostE_Mean", "QSU_PostR_Mean")]
QSU_result <- QSU %>% mutate(., SameValue = QSU_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(QSU_result, "QSU")
```

There is/are `r nrow(QSU_result)` participant(s) have the same value to QSU_PreE_Mean, QSU_PostE_Mean, and QSU_PostR_Mean.

## SHAPS_PreE_Sum SHAPS_PostE_Sum SHAPS_PreE_Mean SHAPS_PostE_Mean
```{r}
index.SHAPS <- data %>% select(., SHAPS_PreE_Sum, SHAPS_PostE_Sum, SHAPS_PreE_Mean, SHAPS_PostE_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
SHAPS <- data[index.SHAPS, c("redcap_id", "SHAPS_PreE_Sum", "SHAPS_PostE_Sum", "SHAPS_PreE_Mean", "SHAPS_PostE_Mean")]
SHAPS_result <- SHAPS %>% mutate(., SameValue = SHAPS_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(SHAPS_result, "SHAPS")
```

There is/are `r nrow(SHAPS_result)` participant(s) have the same value to SHAPS_PreE_Sum, SHAPS_PostE_Sum, SHAPS_PreE_Mean, and SHAPS_PostE_Mean.

## frs_3 to frs_10
```{r}
index.frs <- data %>% select(., frs_3, frs_4, frs_5, frs_6, frs_7, frs_8, frs_9, frs_10) %>% apply(., 1, unique) %>% lapply(., length) == 1
frs <- data[index.frs, c("redcap_id", "frs_3", "frs_4", "frs_5", "frs_6", "frs_7", "frs_8", "frs_9", "frs_10")]
frs_result <- frs %>% mutate(., SameValue = frs_3) %>% select(., redcap_id, SameValue)
Table.Print(frs_result, "frs")
```

There is/are `r nrow(frs_result)` participant(s) have the same value from frs_3 to frs_10.

## postec_crs_1 to postec_crs_11
```{r}
index.crs <- data %>% select(., postec_crs_1, postec_crs_2, postec_crs_3, postec_crs_4, postec_crs_5, postec_crs_6, postec_crs_7, postec_crs_8, postec_crs_9, postec_crs_10, postec_crs_11) %>% apply(., 1, unique) %>% lapply(., length) == 1
crs <- data[index.crs, c("redcap_id", "postec_crs_1", "postec_crs_2", "postec_crs_3", "postec_crs_4", "postec_crs_5", "postec_crs_6", "postec_crs_7", "postec_crs_8", "postec_crs_9", "postec_crs_10", "postec_crs_11")]
crs_result <- crs %>% mutate(., SameValue = postec_crs_1) %>% select(., redcap_id, SameValue)
Table.Print(crs_result, "crs")
```

There is/are `r nrow(crs_result)` participant(s) have the same value from postec_crs_1 to postec_crs_10.

# 4.5%
```{r}
data <- read_sav("/Users/zhan039/Desktop/USC_HEAL/P4/03242020/4.5%_with scoring added_3.23.2020.sav")
```

## MNWS_PreE_Mean MNWS_PostE_Mean MNWS_PostR_Mean
```{r}
# check whether all responses are the same
index.MNWS <- data %>% select(., MNWS_PreE_Mean, MNWS_PostE_Mean, MNWS_PostR_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
MNWS <- data[index.MNWS, c("redcap_id", "MNWS_PreE_Mean", "MNWS_PostE_Mean", "MNWS_PostR_Mean")]
MNWS_result <- MNWS %>% mutate(., SameValue = MNWS_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(MNWS_result, "MNWS")
```

There is/are `r nrow(MNWS_result)` participant(s) have the same value to MNWS_PreE_Mean, MNWS_PostE_Mean, and MNWS_PostR_Mean.

## QSU_PreE_Mean QSU_PostE_Mean QSU_PostR_Mean 
```{r}
index.QSU <- data %>% select(., QSU_PreE_Mean, QSU_PostE_Mean, QSU_PostR_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
QSU <- data[index.QSU, c("redcap_id", "QSU_PreE_Mean", "QSU_PostE_Mean", "QSU_PostR_Mean")]
QSU_result <- QSU %>% mutate(., SameValue = QSU_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(QSU_result, "QSU")
```

There is/are `r nrow(QSU_result)` participant(s) have the same value to QSU_PreE_Mean, QSU_PostE_Mean, and QSU_PostR_Mean.

## SHAPS_PreE_Sum SHAPS_PostE_Sum SHAPS_PreE_Mean SHAPS_PostE_Mean
```{r}
index.SHAPS <- data %>% select(., SHAPS_PreE_Sum, SHAPS_PostE_Sum, SHAPS_PreE_Mean, SHAPS_PostE_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
SHAPS <- data[index.SHAPS, c("redcap_id", "SHAPS_PreE_Sum", "SHAPS_PostE_Sum", "SHAPS_PreE_Mean", "SHAPS_PostE_Mean")]
SHAPS_result <- SHAPS %>% mutate(., SameValue = SHAPS_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(SHAPS_result, "SHAPS")
```

There is/are `r nrow(SHAPS_result)` participant(s) have the same value to SHAPS_PreE_Sum, SHAPS_PostE_Sum, SHAPS_PreE_Mean, and SHAPS_PostE_Mean.

## frs_3 to frs_10
```{r}
index.frs <- data %>% select(., frs_3, frs_4, frs_5, frs_6, frs_7, frs_8, frs_9, frs_10) %>% apply(., 1, unique) %>% lapply(., length) == 1
frs <- data[index.frs, c("redcap_id", "frs_3", "frs_4", "frs_5", "frs_6", "frs_7", "frs_8", "frs_9", "frs_10")]
frs_result <- frs %>% mutate(., SameValue = frs_3) %>% select(., redcap_id, SameValue)
Table.Print(frs_result, "frs")
```

There is/are `r nrow(frs_result)` participant(s) have the same value from frs_3 to frs_10.

## postec_crs_1 to postec_crs_11
```{r}
index.crs <- data %>% select(., postec_crs_1, postec_crs_2, postec_crs_3, postec_crs_4, postec_crs_5, postec_crs_6, postec_crs_7, postec_crs_8, postec_crs_9, postec_crs_10, postec_crs_11) %>% apply(., 1, unique) %>% lapply(., length) == 1
crs <- data[index.crs, c("redcap_id", "postec_crs_1", "postec_crs_2", "postec_crs_3", "postec_crs_4", "postec_crs_5", "postec_crs_6", "postec_crs_7", "postec_crs_8", "postec_crs_9", "postec_crs_10", "postec_crs_11")]
crs_result <- crs %>% mutate(., SameValue = postec_crs_1) %>% select(., redcap_id, SameValue)
Table.Print(crs_result, "crs")
```

There is/are `r nrow(crs_result)` participant(s) have the same value from postec_crs_1 to postec_crs_10.

# 6mg
```{r}
data <- read_sav("/Users/zhan039/Desktop/USC_HEAL/P4/03242020/6mg_with scording added_3.23.2020.sav")
```

## MNWS_PreE_Mean MNWS_PostE_Mean MNWS_PostR_Mean
```{r}
# check whether all responses are the same
index.MNWS <- data %>% select(., MNWS_PreE_Mean, MNWS_PostE_Mean, MNWS_PostR_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
MNWS <- data[index.MNWS, c("redcap_id", "MNWS_PreE_Mean", "MNWS_PostE_Mean", "MNWS_PostR_Mean")]
MNWS_result <- MNWS %>% mutate(., SameValue = MNWS_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(MNWS_result, "MNWS")
```

There is/are `r nrow(MNWS_result)` participant(s) have the same value to MNWS_PreE_Mean, MNWS_PostE_Mean, and MNWS_PostR_Mean.

## QSU_PreE_Mean QSU_PostE_Mean QSU_PostR_Mean 
```{r}
index.QSU <- data %>% select(., QSU_PreE_Mean, QSU_PostE_Mean, QSU_PostR_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
QSU <- data[index.QSU, c("redcap_id", "QSU_PreE_Mean", "QSU_PostE_Mean", "QSU_PostR_Mean")]
QSU_result <- QSU %>% mutate(., SameValue = QSU_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(QSU_result, "QSU")
```

There is/are `r nrow(QSU_result)` participant(s) have the same value to QSU_PreE_Mean, QSU_PostE_Mean, and QSU_PostR_Mean.

## SHAPS_PreE_Sum SHAPS_PostE_Sum SHAPS_PreE_Mean SHAPS_PostE_Mean
```{r}
index.SHAPS <- data %>% select(., SHAPS_PreE_Sum, SHAPS_PostE_Sum, SHAPS_PreE_Mean, SHAPS_PostE_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
SHAPS <- data[index.SHAPS, c("redcap_id", "SHAPS_PreE_Sum", "SHAPS_PostE_Sum", "SHAPS_PreE_Mean", "SHAPS_PostE_Mean")]
SHAPS_result <- SHAPS %>% mutate(., SameValue = SHAPS_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(SHAPS_result, "SHAPS")
```

There is/are `r nrow(SHAPS_result)` participant(s) have the same value to SHAPS_PreE_Sum, SHAPS_PostE_Sum, SHAPS_PreE_Mean, and SHAPS_PostE_Mean.

## frs_3 to frs_10
```{r}
index.frs <- data %>% select(., frs_3, frs_4, frs_5, frs_6, frs_7, frs_8, frs_9, frs_10) %>% apply(., 1, unique) %>% lapply(., length) == 1
frs <- data[index.frs, c("redcap_id", "frs_3", "frs_4", "frs_5", "frs_6", "frs_7", "frs_8", "frs_9", "frs_10")]
frs_result <- frs %>% mutate(., SameValue = frs_3) %>% select(., redcap_id, SameValue)
Table.Print(frs_result, "frs")
```

There is/are `r nrow(frs_result)` participant(s) have the same value from frs_3 to frs_10.

## postec_crs_1 to postec_crs_11
```{r}
index.crs <- data %>% select(., postec_crs_1, postec_crs_2, postec_crs_3, postec_crs_4, postec_crs_5, postec_crs_6, postec_crs_7, postec_crs_8, postec_crs_9, postec_crs_10, postec_crs_11) %>% apply(., 1, unique) %>% lapply(., length) == 1
crs <- data[index.crs, c("redcap_id", "postec_crs_1", "postec_crs_2", "postec_crs_3", "postec_crs_4", "postec_crs_5", "postec_crs_6", "postec_crs_7", "postec_crs_8", "postec_crs_9", "postec_crs_10", "postec_crs_11")]
crs_result <- crs %>% mutate(., SameValue = postec_crs_1) %>% select(., redcap_id, SameValue)
Table.Print(crs_result, "crs")
```

There is/are `r nrow(crs_result)` participant(s) have the same value from postec_crs_1 to postec_crs_10.

# Smoke your Own
```{r}
data <- read_sav("/Users/zhan039/Desktop/USC_HEAL/P4/03242020/Smoker your own_with scoring added_3.23.2020.sav")
```

## MNWS_PreE_Mean MNWS_PostE_Mean MNWS_PostR_Mean
```{r}
# check whether all responses are the same
index.MNWS <- data %>% select(., MNWS_PreE_Mean, MNWS_PostE_Mean, MNWS_PostR_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
MNWS <- data[index.MNWS, c("redcap_id", "MNWS_PreE_Mean", "MNWS_PostE_Mean", "MNWS_PostR_Mean")]
MNWS_result <- MNWS %>% mutate(., SameValue = MNWS_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(MNWS_result, "MNWS")
```

There is/are `r nrow(MNWS_result)` participant(s) have the same value to MNWS_PreE_Mean, MNWS_PostE_Mean, and MNWS_PostR_Mean.

## QSU_PreE_Mean QSU_PostE_Mean QSU_PostR_Mean 
```{r}
index.QSU <- data %>% select(., QSU_PreE_Mean, QSU_PostE_Mean, QSU_PostR_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
QSU <- data[index.QSU, c("redcap_id", "QSU_PreE_Mean", "QSU_PostE_Mean", "QSU_PostR_Mean")]
QSU_result <- QSU %>% mutate(., SameValue = QSU_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(QSU_result, "QSU")
```

There is/are `r nrow(QSU_result)` participant(s) have the same value to QSU_PreE_Mean, QSU_PostE_Mean, and QSU_PostR_Mean.

## SHAPS_PreE_Sum SHAPS_PostE_Sum SHAPS_PreE_Mean SHAPS_PostE_Mean
```{r}
index.SHAPS <- data %>% select(., SHAPS_PreE_Sum, SHAPS_PostE_Sum, SHAPS_PreE_Mean, SHAPS_PostE_Mean) %>% apply(., 1, unique) %>% lapply(., length) == 1
SHAPS <- data[index.SHAPS, c("redcap_id", "SHAPS_PreE_Sum", "SHAPS_PostE_Sum", "SHAPS_PreE_Mean", "SHAPS_PostE_Mean")]
SHAPS_result <- SHAPS %>% mutate(., SameValue = SHAPS_PreE_Mean) %>% select(., redcap_id, SameValue)
Table.Print(SHAPS_result, "SHAPS")
```

There is/are `r nrow(SHAPS_result)` participant(s) have the same value to SHAPS_PreE_Sum, SHAPS_PostE_Sum, SHAPS_PreE_Mean, and SHAPS_PostE_Mean.

## frs_3 to frs_10
```{r}
index.frs <- data %>% select(., frs_3, frs_4, frs_5, frs_6, frs_7, frs_8, frs_9, frs_10) %>% apply(., 1, unique) %>% lapply(., length) == 1
frs <- data[index.frs, c("redcap_id", "frs_3", "frs_4", "frs_5", "frs_6", "frs_7", "frs_8", "frs_9", "frs_10")]
frs_result <- frs %>% mutate(., SameValue = frs_3) %>% select(., redcap_id, SameValue)
Table.Print(frs_result, "frs")
```

There is/are `r nrow(frs_result)` participant(s) have the same value from frs_3 to frs_10.

## postec_crs_1 to postec_crs_11
```{r}
index.crs <- data %>% select(., postec_crs_1, postec_crs_2, postec_crs_3, postec_crs_4, postec_crs_5, postec_crs_6, postec_crs_7, postec_crs_8, postec_crs_9, postec_crs_10, postec_crs_11) %>% apply(., 1, unique) %>% lapply(., length) == 1
crs <- data[index.crs, c("redcap_id", "postec_crs_1", "postec_crs_2", "postec_crs_3", "postec_crs_4", "postec_crs_5", "postec_crs_6", "postec_crs_7", "postec_crs_8", "postec_crs_9", "postec_crs_10", "postec_crs_11")]
crs_result <- crs %>% mutate(., SameValue = postec_crs_1) %>% select(., redcap_id, SameValue)
Table.Print(crs_result, "crs")
```

There is/are `r nrow(crs_result)` participant(s) have the same value from postec_crs_1 to postec_crs_10.