---
title: "SmokeYourOwn_inconsistency"
author: "Yi"
date: "3/30/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
library(haven)
library(tidyverse)
```

```{r}
data <- read_sav("/Users/zhan039/Desktop/USC_HEAL/P4/03242020/Smoker your own_with scoring added_3.23.2020.sav")
```

```{r}
Table.Print <- function(table, title) {
  if (nrow(table) > 0) {
    knitr::kable(table, caption = title)
  }
}
```

## preec_panas
- check whether all responses are same.
```{r}
# check whether all responses to PANAS Pre E are the same
index.preec_panas <- data %>% select(., starts_with("preec_panas")) %>% apply(., 1, unique) %>% lapply(., length) == 1
PANAS_PreE <- data[index.preec_panas, c("redcap_id", colnames(data)[startsWith(colnames(data), "preec_panas")])]
PANAS_PreE_result <- PANAS_PreE %>% mutate(., SameValue = preec_panas_1) %>% select(., redcap_id, SameValue)
Table.Print(PANAS_PreE_result, "preec_panas")
```

There are `r nrow(PANAS_PreE_result)` participant(s) responded the same value to all preec_panas questions.

- check whether any PA >= 3 and any NA >= 3 / any PA < 3 and andy NA < 3
```{r}
preec_panas <- select(data, starts_with("preec_panas"))

# compare each item with 3
preec_panas_bi <- as.data.frame(ifelse(preec_panas >= 3, 1, 0))

# sum the results for PA and NA
preec_panas_bi_sum <- mutate(preec_panas_bi, PA_sum = preec_panas_1 + preec_panas_3 + preec_panas_5 + preec_panas_9 + preec_panas_10 + preec_panas_12 + preec_panas_14 + preec_panas_16 + preec_panas_17 +  preec_panas_19, NA_sum = preec_panas_2 + preec_panas_4 + preec_panas_6 + preec_panas_7 + preec_panas_8 + preec_panas_11 + preec_panas_13 + preec_panas_15 + preec_panas_18 + preec_panas_20)

# find the inconsistency
preec_panas_compare <- mutate(preec_panas_bi_sum, preec_panas_inconsist = ifelse((PA_sum > 0) == (NA_sum > 0), 1, 0))

# cbind the information
preec_panas_inconsis <- cbind(data, preec_panas_compare$preec_panas_inconsist)
colnames(preec_panas_inconsis)[length(colnames(preec_panas_inconsis))] <- "preec_panas_inconsistency"

# get the redcap id
preec_panas_result <- preec_panas_inconsis %>% filter(., preec_panas_inconsistency > 0) %>% select(., redcap_id)
Table.Print(preec_panas_result, "Inconsistency of preec_panas Variables")
```

There are `r nrow(preec_panas_result)` participant(s) have same directions of PA and NA (both >= 3 or < 3). 

- check whether difference of PA sum and NA sum <= 5
```{r}
# check whether difference of PA and NA <= 5
PANAS.PreE.difference <- data[abs(data$PANAS_PreE_PA - data$PANAS_PreE_NA) <= 5, c("redcap_id", "PANAS_PreE_PA", "PANAS_PreE_NA")]
Table.Print(PANAS.PreE.difference, "Inconsistency of preec_panas Variables")
```

There are `r nrow(PANAS.PreE.difference)` participant(s) have similar sum scores of PA and NA (differences <= 5). 

## postec_panas
- check whether all responses are same
```{r}
index.postec_panas <- data %>% select(., starts_with("postec_panas")) %>% apply(., 1, unique) %>% lapply(., length) == 1
PANAS_PostE <- data[index.postec_panas, c("redcap_id", colnames(data)[startsWith(colnames(data), "postec_panas")])]
PANAS_PostE_result <- PANAS_PostE %>% mutate(., SameValue = postec_panas_1) %>% select(., redcap_id, SameValue)
Table.Print(PANAS_PostE_result, "postec_panas")
```

There are `r nrow(PANAS_PostE_result)` participant(s) responded the same value to all postec_panas questions.

- check whether any PA >= 3 and any NA >= 3 / any PA < 3 and andy NA < 3
```{r}
postec_panas <- select(data, starts_with("postec_panas"))

# compare each item with 3
postec_panas_bi <- as.data.frame(ifelse(postec_panas >= 3, 1, 0))

# sum the results for PA and NA
postec_panas_bi_sum <- mutate(postec_panas_bi, PA_sum = postec_panas_1 + postec_panas_3 + postec_panas_5 + postec_panas_9 + postec_panas_10 + postec_panas_12 + postec_panas_14 + postec_panas_16 + postec_panas_17 +  postec_panas_19, NA_sum = postec_panas_2 + postec_panas_4 + postec_panas_6 + postec_panas_7 + postec_panas_8 + postec_panas_11 + postec_panas_13 + postec_panas_15 + postec_panas_18 + postec_panas_20)

# find the inconsistency
postec_panas_compare <- mutate(postec_panas_bi_sum, postec_panas_inconsist = ifelse((PA_sum > 0) == (NA_sum > 0), 1, 0))

# cbind the information
postec_panas_inconsis <- cbind(data, postec_panas_compare$postec_panas_inconsist)
colnames(postec_panas_inconsis)[length(colnames(postec_panas_inconsis))] <- "postec_panas_inconsistency"

# get the redcap id
postec_panas_result <- postec_panas_inconsis %>% filter(., postec_panas_inconsistency > 0) %>% select(., redcap_id)
Table.Print(postec_panas_result, "Inconsistency of postec_panas Variables")
```

There are `r nrow(postec_panas_result)` participant(s) have same directions of PA and NA (both >= 3 or < 3). 

- check whether difference of PA sum and NA sum <= 5
```{r}
# check whether difference of PA and NA <= 5
PANAS.PostE.difference <- data[abs(data$PANAS_PostE_PA - data$PANAS_PostE_NA) <= 5, c("redcap_id", "PANAS_PostE_PA", "PANAS_PostE_NA")]
Table.Print(PANAS.PostE.difference, "Inconsistency of postec_panas Variables")
```

There are `r nrow(PANAS.PostE.difference)` participant(s) have similar sum scores of PA and NA (differences <= 5). 


## prer_panas
- check whether all responses are same
```{r}
index.prer_panas <- data %>% select(., starts_with("prer_panas")) %>% apply(., 1, unique) %>% lapply(., length) == 1
PANAS_PostR <- data[index.prer_panas, c("redcap_id", colnames(data)[startsWith(colnames(data), "prer_panas")])]
PANAS_PostR_result <- PANAS_PostR %>% mutate(., SameValue = prer_panas_1) %>% select(., redcap_id, SameValue)
Table.Print(PANAS_PostR_result, "prer_panas")
```

There are `r nrow(PANAS_PostR_result)` participant(s) responded the same value to all prer_panas questions.

- check whether any PA >= 3 and any NA >= 3 / any PA < 3 and andy NA < 3
```{r}
prer_panas <- select(data, starts_with("prer_panas"))

# compare each item with 3
prer_panas_bi <- as.data.frame(ifelse(prer_panas >= 3, 1, 0))

# sum the results for PA and NA
prer_panas_bi_sum <- mutate(prer_panas_bi, PA_sum = prer_panas_1 + prer_panas_3 + prer_panas_5 + prer_panas_9 + prer_panas_10 + prer_panas_12 + prer_panas_14 + prer_panas_16 + prer_panas_17 +  prer_panas_19, NA_sum = prer_panas_2 + prer_panas_4 + prer_panas_6 + prer_panas_7 + prer_panas_8 + prer_panas_11 + prer_panas_13 + prer_panas_15 + prer_panas_18 + prer_panas_20)

# find the inconsistency
prer_panas_compare <- mutate(prer_panas_bi_sum, prer_panas_inconsist = ifelse((PA_sum > 0) == (NA_sum > 0), 1, 0))

# cbind the information
prer_panas_inconsis <- cbind(data, prer_panas_compare$prer_panas_inconsist)
colnames(prer_panas_inconsis)[length(colnames(prer_panas_inconsis))] <- "prer_panas_inconsistency"

# get the redcap id
prer_panas_result <- prer_panas_inconsis %>% filter(., prer_panas_inconsistency > 0) %>% select(., redcap_id)
Table.Print(prer_panas_result, "Inconsistency of prer_panas Variables")
```

There are `r nrow(prer_panas_result)` participant(s) have same directions of PA and NA (both >= 3 or < 3). 

- check whether difference of PA sum and NA sum <= 5
```{r}
# check whether difference of PA and NA <= 5
PANAS.PostR.difference <- data[abs(data$PANAS_PostR_PA - data$PANAS_PostR_NA) <= 5, c("redcap_id", "PANAS_PostR_PA", "PANAS_PostR_NA")]
Table.Print(PANAS.PostR.difference, "Inconsistency of prer_panas Variables")
```

There are `r nrow(PANAS.PostR.difference)` participant(s) have similar sum scores of PA and NA (differences <= 5). 

## prec_cis
- check whether all responses are same
```{r}
index.prec_cis <- data %>% select(., starts_with("prec_cis")) %>% apply(., 1, unique) %>% lapply(., length) == 1
PreE_CIS <- data[index.prec_cis, c("redcap_id", colnames(data)[startsWith(colnames(data), "prec_cis")])]
PreE_CIS_result <- PreE_CIS %>% mutate(., SameValue = prec_cis_1) %>% select(., redcap_id, SameValue)
Table.Print(PreE_CIS_result, "prec_cis")
```

There are `r nrow(PreE_CIS_result)` participant(s) responded the same value to all prec_cis questions.

- check whether any PA >= 2 and any NA >= 2 / any PA <= 2 and andy NA <= 2
```{r}
prec_cis <- select(data, starts_with("prec_cis"))

# compare each item with 3
prec_cis_bi <- as.data.frame(ifelse(prec_cis >= 2, 1, 0))

# sum the results for PA and NA
prec_cis_bi_sum <- mutate(prec_cis_bi, PA_sum = prec_cis_4 + prec_cis_5 + prec_cis_6 + prec_cis_8 + prec_cis_10 + prec_cis_12 + prec_cis_15 + prec_cis_18 + prec_cis_19, NA_sum = prec_cis_1 + prec_cis_2 + prec_cis_3 + prec_cis_7 + prec_cis_9 + prec_cis_11 + prec_cis_13 + prec_cis_14 + prec_cis_16 + prec_cis_17)

# find the inconsistency
prec_cis_compare <- mutate(prec_cis_bi_sum, prec_cis_inconsist = ifelse((PA_sum > 0) == (NA_sum > 0), 1, 0))

# cbind the information
prec_cis_inconsis <- cbind(data, prec_cis_compare$prec_cis_inconsist)
colnames(prec_cis_inconsis)[length(colnames(prec_cis_inconsis))] <- "prec_cis_inconsistency"

# get the redcap id
prec_cis_result <- prec_cis_inconsis %>% filter(., prec_cis_inconsistency > 0) %>% select(., redcap_id)
Table.Print(prec_cis_result, "Inconsistency of prec_cis Variables")
```

There are `r nrow(prec_cis_result)` participant(s) have same directions of PA and NA (both >= 2 or < 2). 

## postec_cis
- check whether all responses are same
```{r}
index.postec_cis <- data %>% select(., starts_with("postec_cis")) %>% apply(., 1, unique) %>% lapply(., length) == 1
PostE_CIS <- data[index.postec_cis, c("redcap_id", colnames(data)[startsWith(colnames(data), "postec_cis")])]
PostE_CIS_result <- PostE_CIS %>% mutate(., SameValue = postec_cis_1) %>% select(., redcap_id, SameValue)
Table.Print(PostE_CIS_result, "postec_cis")
```

There are `r nrow(PostE_CIS_result)` participant(s) responded the same value to all prec_cis questions.

- check whether any PA >= 2 and any NA >= 2 / any PA <= 2 and andy NA <= 2
```{r}
postec_cis <- select(data, starts_with("postec_cis"))

# compare each item with 3
postec_cis_bi <- as.data.frame(ifelse(postec_cis >= 2, 1, 0))

# sum the results for PA and NA
postec_cis_bi_sum <- mutate(postec_cis_bi, PA_sum = postec_cis_4 + postec_cis_5 + postec_cis_6 + postec_cis_8 + postec_cis_10 + postec_cis_12 + postec_cis_15 + postec_cis_18 + postec_cis_19, NA_sum = postec_cis_1 + postec_cis_2 + postec_cis_3 + postec_cis_7 + postec_cis_9 + postec_cis_11 + postec_cis_13 + postec_cis_14 + postec_cis_16 + postec_cis_17)

# find the inconsistency
postec_cis_compare <- mutate(postec_cis_bi_sum, postec_cis_inconsist = ifelse((PA_sum > 0) == (NA_sum > 0), 1, 0))

# cbind the information
postec_cis_inconsis <- cbind(data, postec_cis_compare$postec_cis_inconsist)
colnames(postec_cis_inconsis)[length(colnames(postec_cis_inconsis))] <- "postec_cis_inconsistency"

# get the redcap id
postec_cis_result <- postec_cis_inconsis %>% filter(., postec_cis_inconsistency > 0) %>% select(., redcap_id)
Table.Print(postec_cis_result, "Inconsistency of postec_cis Variables")
```

There are `r nrow(postec_cis_result)` participant(s) have same directions of PA and NA (both >= 2 or < 2). 

## FRS
- check whether frs_1 = frs_2
```{r}
frs_1_2 <- select(data, redcap_id, frs_1, frs_2)
frs_1_2_inconsis <- filter(frs_1_2, frs_1 == frs_2)
Table.Print(frs_1_2_inconsis, "Inconsistency of frs_1 and frs_2")
```

There are `r nrow(frs_1_2_inconsis)` participant(s) responded the same value to frs_1 and frs_2 questions.