---
title: "Pilot 2 - Prolific "
author: "Yi"
date: "5/27/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(kableExtra)
library(ggplot2)
```

```{r}
data <- read.csv('/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04292020/Prolific2.csv', na.strings = "")
```


```{r}
# create the redcap survey time
CreateRCtime <- function(platform) {
  time.ncol <- ends_with("timestamp", vars = colnames(platform))
  start <- time.ncol[1]
  end <- time.ncol[length(time.ncol)]

  platform$start.time <- strptime(platform[, start], format = "%Y-%m-%d %H:%M:%S") 
  platform$end.time <- strptime(platform[, end], format = "%Y-%m-%d %H:%M:%S")

  platform$diff.time <- difftime(platform$end.time, platform$start.time, units = "secs")
  platform$diff.time <- as.numeric(platform$diff.time)
  
  return(platform)
}

data <- CreateRCtime(data)
```


```{r}
### result of each attention check question
## success
data <- mutate(data, att1.success = ifelse(data$att_check1___1 == 1 & data$att_check1___4 == 1 & data$att_check1___5 == 1, 1, 0))

data <- mutate(data, att2.success = ifelse(data$last_30_ecig_yn == 1 & data$att_check2 == 3, 1, ifelse(data$last_30_ecig_yn == 1, 0, NA))) # people who are not asked the second question are marked as NA

data <- mutate(data, att3a.success = ifelse(data$att_check3a == 4, 1, 0))

data <- mutate(data, att3b.success = ifelse(grepl("decision making", data$att_check3b, ignore.case = T), 1, ifelse(data$att_check3a == 4, 0, NA)))

data <- mutate(data, att3.success = ifelse(data$att_check3a == 4 & grepl("decision making", data$att_check3b, ignore.case = T), 1, 0))

## failure
data <- mutate(data, att1.fail = ifelse(!(data$att_check1___1 == 1 & data$att_check1___4 == 1 & data$att_check1___5 == 1), 1, 0))

# data[!is.na(data$att_check2), "last_30_ecig_yn"]
data <- mutate(data, att2.fail = ifelse(data$last_30_ecig_yn == 1 & data$att_check2 != 3, 1, ifelse(data$last_30_ecig_yn == 1, 0, NA))) # people who are not asked the second question are marked as NA

data <- mutate(data, att3a.fail = ifelse(data$att_check3a != 4, 1, 0))

# data[!is.na(data$att_check3b), "att_check3a"]
data <- mutate(data, att3b.fail = ifelse(grepl("decision making", data$att_check3b, ignore.case = T), 0, ifelse(data$att_check3a == 4, 1, NA)))

data <- mutate(data, att3.fail = ifelse(!(data$att_check3a == 4 & grepl("decision making", data$att_check3b, ignore.case = T)), 1, 0))
```

### 1 & 2 & 3 & 4. N(%) who fail the attention checks
```{r}

FreqPerc1 <- function(platform,varname) {
  freq <- table(select(platform, all_of(varname)), useNA = "always")
  perct <- round(prop.table(freq) * 100, 1)
  nperct <- paste(freq, " ", "(", perct, "%", ")", sep = "")
  nperct <- as.vector(nperct)
  nperct[4] <- sum(!is.na(platform$redcapid))
  return(nperct)
}

FreqPerc2 <- function(platform, varname) {
  freq <- table(select(platform, all_of(varname)), useNA = "no")
  perct <- round(prop.table(freq) * 100, 1)
  nperct <- paste(freq, " ", "(", perct, "%", ")", sep = "")
  nperct <- as.vector(nperct)
  nperct[3] <- "0 (0%)"
  nperct[4] <- sum(!is.na(select(platform, all_of(varname))))
  return(nperct)
}

att1 <- FreqPerc1(data, "att1.fail")
last_30_ecig_yn <- FreqPerc1(data, "last_30_ecig_yn")
att2_1 <- FreqPerc1(data, "att2.fail") # among all participants
att2_2 <- FreqPerc2(data, "att2.fail") # only among [last_30_ecig_yn] = '1'
att3a <- FreqPerc1(data, "att3a.fail")
att3b_1 <- FreqPerc1(data, "att3b.fail")
att3b_2 <- FreqPerc2(data, "att3b.fail")
table1 <- as.data.frame(cbind(att1, att2_1, att2_2, att3a, att3b_2))

colnames(table1) <- c("First", paste0("Second", footnote_marker_alphabet(1)), paste0("Second", footnote_marker_alphabet(2)), "Third", paste0("Fourth", footnote_marker_alphabet(3)))
rownames(table1) <- c("Success", "Failure", "Missing", "Total")

kableExtra::kable(table1, escape = F, caption = "N(%) of Attention Check Questions Failures", align = "c") %>% footnote(alphabet = c("Among all participants", "Only among participants who saw it (last_30_ecig_yn = 1)", "Variable name of the fourth attention check: att_check_3b")) %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% row_spec(2, bold = T)
```


### 5 & 6 & 7. N(%) who are considered "bots" on the MaxDiff tasks

Among all participants in the Redcap (N = 332), 302 participants have valid information on all three bot status in the Maxdiff pilot 2 dataset, which is the same as the sample size of Maxdiff pilot 2 dataset (N = 302). 

```{r}
bot <- readRDS("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04232020/MaxDiff_Pilot2_BotFit.rds")

mergedata <- left_join(data, bot, by = "redcapid")

# sum(is.na(mergedata$md_device_fit_cut))
# sum(is.na(mergedata$md_eliquid_fit_cut))
# sum(is.na(mergedata$md_reason_fit_cut))
# sum(is.na(mergedata$md_device_fit_cut) & is.na(mergedata$md_eliquid_fit_cut) & is.na(mergedata$md_reason_fit_cut))



maxdiff1 <- FreqPerc1(mergedata, "md_device_fit_cut")
maxdiff2 <- FreqPerc1(mergedata, "md_eliquid_fit_cut")
maxdiff3 <- FreqPerc1(mergedata, "md_reason_fit_cut")
table2 <- as.data.frame(cbind(maxdiff1, maxdiff2, maxfdiff3))
colnames(table2) <- c("The First MaxDiff (device)", "The Second MaxDiff (liquids)", "The Third MaxDiff (reasons)")
rownames(table2) <- c("Not bot", "Bot", "Missing", "Total")

kableExtra::kable(table2, caption = "N(%) of Bots", align = "c") %>% row_spec(2, bold = T) %>% kable_styling(bootstrap_options = "striped", full_width = F)
```

### 8. Check for ouliers of REDCap survey time with 2SD and mean completion time
```{r}
# outliers
RC.mean <- mean(data$diff.time, na.rm = T)
RC.sd <- sd(data$diff.time, na.rm = T)
RC.low <- RC.mean - 2 * RC.sd
RC.upp <- RC.mean + 2 * RC.sd
RC.mean.sd <- rbind(RC.mean, RC.sd, RC.low, RC.upp)

rownames(RC.mean.sd) <- c("Mean", "SD", "Mean - 2SD", "Mean + 2SD")
colnames(RC.mean.sd) <- paste0("Redcap Survey Time (in secs)", footnote_marker_alphabet(1))

kableExtra::kable(RC.mean.sd, escape = F,caption = "Summary of Redcap Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% footnote(alphabet = "From the start of \"Work Id\" section to the start of \"Advertisements\" section")

# NA
RC.mean.na <- data[is.na(data$diff.time), c("redcapid", "diff.time")]

colnames(RC.mean.na)[2] <- paste0("Redcap Survey Time (in secs)", footnote_marker_alphabet(1))
rownames(RC.mean.na) <- NULL

kableExtra::kable(RC.mean.na, escape = F, caption = "Participants Who Have Missing Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% footnote(alphabet = "From the start of \"Work Id\" section to the start of \"Advertisements\" section")

```

Based on the information above (mean - 2SD, mean + 2SD), potential outliers are listed below.
```{r}
RC.mean.outliers <- data[which(data$diff.time > RC.upp | data$diff.time < RC.low), c("redcapid", "diff.time")]

colnames(RC.mean.outliers)[2] <- paste0("Redcap Survey Time (in secs)", footnote_marker_alphabet(1))
rownames(RC.mean.outliers) <- NULL

kableExtra::kable(RC.mean.outliers, escape = F, caption = "Potential Outliers (defined by mean + 2SD and mean - 2SD)", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% footnote(alphabet = "From the start of \"Work Id\" section to the start of \"Advertisements\" section")

# prepare for the question 12 - 14
mergedata <- mutate(mergedata, RC.mean.outliers = ifelse(mergedata$redcapid %in% RC.mean.outliers$redcapid, 1, 0))
```

### 9. Check for ouliers of Sawtooth survey time with 2SD and mean completion time
```{r}
# outliers
ST.mean <- mean(mergedata$md_time_inSec, na.rm = T)
ST.sd <- sd(mergedata$md_time_inSec, na.rm = T)
ST.low <- ST.mean - 2 * ST.sd
ST.upp <- ST.mean + 2 * ST.sd
ST.mean.sd <- rbind(ST.mean, ST.sd, ST.low, ST.upp)

rownames(ST.mean.sd) <- c("Mean", "SD", "Mean - 2SD", "Mean + 2SD")
colnames(ST.mean.sd) <- "Sawtooth Survey Time (in secs)"

kableExtra::kable(ST.mean.sd, escape = F,caption = "Summary of Sawtooth Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F)

# NA
ST.mean.na <- mergedata[is.na(mergedata$md_time_inSec), c("redcapid", "md_time_inSec")]

colnames(ST.mean.na)[2] <- "Sawtooth Survey Time (in secs)"
rownames(ST.mean.na) <- NULL

kableExtra::kable(ST.mean.na, caption = "Participants Who Have Missing Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F)

```

Based on the information above (mean - 2SD, mean + 2SD), potential outliers are listed below.
```{r}
ST.mean.outliers <- mergedata[which(mergedata$md_time_inSec > ST.upp | mergedata$md_time_inSec < ST.low), c("redcapid", "md_time_inSec")]

colnames(ST.mean.outliers)[2] <- "Sawtooth Survey Time (in secs)"
rownames(ST.mean.outliers) <- NULL

kableExtra::kable(ST.mean.outliers, caption = "Potential Outliers (defined by mean + 2SD and mean - 2SD)", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F)

# prepare for questions 12 - 14
mergedata <- mutate(mergedata, ST.mean.outliers = ifelse(mergedata$redcapid %in% ST.mean.outliers$redcapid, 1, 0))
```

### 10. Check for ouliers of REDCap survey time 
```{r}
ggplot(data = data, aes(y = diff.time)) + geom_boxplot(na.rm = T) + theme(axis.text.x = element_blank()) + labs(y = "Redcap Survey Time (in secs)", title = "Boxplot of REDCap Survey Time") + xlim(-1, 1)
```

<br>
```{r}
RC.qtile <- quantile(data$diff.time, probs = c(0.25, 0.75), na.rm = TRUE)
RC.iqr <- IQR(data$diff.time, na.rm = T)
RC.iqr.upp <- RC.qtile[2]  + 1.5 * RC.iqr
RC.iqr.low <- RC.qtile[1] - 1.5 * RC.iqr
RC.iqr.ex.upp <- RC.qtile[2] + 3 * RC.iqr
RC.iqr.ex.low <- RC.qtile[1] - 3 * RC.iqr
RC.iqr.bound<- rbind(RC.iqr.upp, RC.iqr.low, RC.iqr.ex.upp, RC.iqr.ex.low)
colnames(RC.iqr.bound) <- paste0("Redcap Survey Time (in secs)", footnote_marker_alphabet(1))
rownames(RC.iqr.bound) <- c("Q3 + 1.5 * IQR", "Q1 - 1.5 * IQR", "Q3 + 3 * IQR", "Q1 - 3 * IQR")

kableExtra::kable(RC.iqr.bound, escape = F, caption = "Summary of REDCap survey time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% footnote(alphabet = "From the start of \"Work Id\" section to the start of \"Advertisements\" section")

kableExtra::kable(RC.mean.na, escape = F, caption = "Participants Who Have Missing Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% footnote(alphabet = "From the start of \"Work Id\" section to the start of \"Advertisements\" section")

```

Based on the information above (Q1 - 1.5 * IQR, Q3 + 1.5 * IQR), the potential outliers are listed below.
```{r}
RC.iqr.outliers <- data[which(data$diff.time > RC.iqr.upp | data$diff.time < RC.iqr.low), c("redcapid", "diff.time")]

RC.iqr.outliers <- mutate(RC.iqr.outliers,  diff.time = ifelse(diff.time > RC.iqr.ex.upp | diff.time < RC.iqr.ex.low, paste0(diff.time, footnote_marker_symbol(1, format = "html")), diff.time))

colnames(RC.iqr.outliers)[2] <- paste0("Redcap Survey Time (in secs)", footnote_marker_alphabet(1))
rownames(RC.iqr.outliers) <- NULL

kableExtra::kable(RC.iqr.outliers, escape = F, format = "html", caption = "Potential Outliers (defined by Q3 + 1.5 * IQR and Q1 - 1.5 * IQR)", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% footnote(symbol = "These are values larger than Q3 + 3 `*` IQR or smaller than Q1 - 3`*` IQR", alphabet = "From the start of \"Work Id\" section to the start of \"Advertisements\" section" )

# prepare for questions 12 - 14
mergedata <- mutate(mergedata, RC.iqr.outliers = ifelse(mergedata$redcapid %in% RC.iqr.outliers$redcapid, 1, 0))
```

### 11. Check for ouliers of Sawtooth survey time 
```{r}
ggplot(data = mergedata, aes(y = md_time_inSec)) + geom_boxplot(na.rm = T) + theme(axis.text.x = element_blank()) + labs(y = "Sawtooth Survey Time (in secs)", title = "Boxplot of Sawtooth Survey Time") + xlim(-1, 1)
```

<br>
```{r}
ST.qtile <- quantile(mergedata$md_time_inSec, probs = c(0.25, 0.75), na.rm = T)
ST.iqr <- IQR(mergedata$md_time_inSec, na.rm = T)
ST.iqr.upp <- ST.qtile[2] + 1.5 * ST.iqr
ST.iqr.low <- ST.qtile[1] - 1.5 * ST.iqr
ST.iqr.ex.upp <- ST.qtile[2] + 3 * ST.iqr
ST.iqr.ex.low <- ST.qtile[1] - 3 * ST.iqr
ST.iqr.bound <- rbind(ST.iqr.upp, ST.iqr.low, ST.iqr.ex.upp, ST.iqr.ex.low)
colnames(ST.iqr.bound) <- "Sawtooth Survey Time (in secs)"
rownames(ST.iqr.bound) <- c("Q3 + 1.5 * IQR", "Q1 - 1.5 * IQR", "Q3 + 3 * IQR", "Q1 - 3 * IQR")

kableExtra::kable(ST.iqr.bound, caption = "Summary of Sawtooth Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F)

kableExtra::kable(ST.mean.na, caption = "Participants Who Have Missing Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F)

```

Based on the information above (Q1 - 1.5 * IQR, Q3 + 1.5 * IQR), the potential outliers are listed below.
```{r}
ST.iqr.outliers <- mergedata[which(mergedata$md_time_inSec > ST.iqr.upp | mergedata$md_time_inSec < ST.iqr.low), c("redcapid", "md_time_inSec")]

ST.iqr.outliers <- mutate(ST.iqr.outliers, md_time_inSec = ifelse(md_time_inSec > ST.iqr.ex.upp | md_time_inSec < ST.iqr.ex.low, paste0(md_time_inSec, footnote_marker_symbol(1)), md_time_inSec))

colnames(ST.iqr.outliers)[2] <- "Sawtooth Survey Time (in secs)"
rownames(ST.iqr.outliers) <- NULL

kableExtra::kable(ST.iqr.outliers, escape = F, caption = "Potential Outliers (defined by Q3 + 1.5 * IQR and Q1 - 1.5 * IQR)", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% footnote(symbol = "These are values larger than Q3 + 3 `*` IQR or smaller than Q1 - 3`*` IQR")

# prepare for questions 12 - 14
mergedata <- mutate(mergedata, ST.iqr.outliers = ifelse(mergedata$redcapid %in% ST.iqr.outliers$redcapid, 1, 0))
```

### 12. Distribution of number of criteria met for items 1-11 (count of "yes")
```{r}
mergedata$count.1.11 <- apply(mergedata[, c("att1.fail", "att2.fail", "att3a.fail", "att3b.fail", "md_device_fit_cut", "md_eliquid_fit_cut", "md_reason_fit_cut", "RC.mean.outliers", "ST.mean.outliers", "RC.iqr.outliers", "ST.iqr.outliers")], 1, sum, na.rm = T)

# kableExtra::kable(mergedata[, c("att1.fail", "att2.fail", "att3a.fail", "att3b.fail", "md_fit_cut", "RC.mean.outliers", "ST.mean.outliers", "RC.iqr.outliers", "ST.iqr.outliers", "count.1.11")]) %>% kable_styling(bootstrap_options = "striped", full_width = F) %>% scroll_box( height = "500px")

ggplot(data = mergedata, aes(x = count.1.11)) +  geom_histogram(binwidth = 0.5) + labs(x = "Count of 'Yes'", y = "Frequency", title = "Distribution of number of criteria met for items 1-11 ") + scale_x_continuous(breaks = sort(unique(mergedata$count.1.11)), labels = sort(unique(mergedata$count.1.11)))
```

### 13. Distribution of number of criteria met for items 1-9
```{r}
mergedata$count.1.9 <- apply(mergedata[, c("att1.fail", "att2.fail", "att3a.fail", "att3b.fail", "md_device_fit_cut", "md_eliquid_fit_cut", "md_reason_fit_cut", "RC.mean.outliers", "ST.mean.outliers")], 1, sum, na.rm = T)

ggplot(data = mergedata, aes(x = count.1.9)) + geom_histogram(binwidth = 0.5) + labs(x = "Count of 'Yes'", y = "Frequency", title = "Distribution of number of criteria met for items 1-9")
```

## 14. Distribution of number of criteria met for items 1-7 and 10-11
```{r}
mergedata$count.1.7 <- apply(mergedata[, c("att1.fail", "att2.fail", "att3a.fail", "att3b.fail", "md_device_fit_cut", "md_eliquid_fit_cut", "md_reason_fit_cut")], 1, sum, na.rm = T)

ggplot(data = mergedata, aes(x = count.1.7)) + geom_histogram(binwidth = 0.5) + labs(x = "Count of 'Yes'", y = "Frequency", title = "Distribution of number of criteria met for items 1-7")
```

```{r}
mergedata$count.10.11 <- apply(mergedata[, c("RC.iqr.outliers", "ST.iqr.outliers")], 1, sum, na.rm = T)

ggplot(data = mergedata, aes(x = count.10.11)) + geom_histogram(binwidth = 0.5) + labs(x = "Count of 'Yes'", y = "Frequency", title = "Distribution of number of criteria met for items 10-11") + scale_x_continuous(breaks = sort(unique(mergedata$count.10.11)), labels = sort(unique(mergedata$count.10.11)))
```

