---
title: "HH poster"
author: "Yi"
date: "4/9/2020"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include=FALSE}
library(haven)
library(tidyverse)
```

```{r}
data <- read_sas("/Users/zhan039/Desktop/USC_HEAL/HH/04072020/HH_W9_Scored.sas7bdat")
```

## XX% use social media on a daily basis
```{r}
SocialMedia <- select(data, record_id, starts_with("W9_Social"))

  # check the coding
  # apply(SocialMedia[, -1], 2, table)

# exclude "specify:"
SocialMedia.di <- SocialMedia[, c(1:(ncol(SocialMedia)-1))]

# create the dichotomous variable: Several times a day / daily = 1; Others = 0
for (i in c(2: ncol(SocialMedia.di))) {
  newvar <- paste(names(SocialMedia.di[, i]), "_di", sep = "")
  SocialMedia.di[, newvar] <- ifelse(SocialMedia.di[, i] == 2 | SocialMedia.di[, i] == 3, 1, 0)
}

SocialMedia.count <- select(SocialMedia.di, record_id, ends_with("_di"))

# People who didn't answer this section
SocialMedia.count.NA <- filter(SocialMedia.count, is.na(W9_Social_Facebook_di) & is.na(W9_Social_Instagram_di) & is.na(W9_Social_Twitter_di) & is.na(W9_Social_Linkedin_di) & is.na(W9_Social_Pinterest_di) & is.na(W9_Social_Snapchat_di) & is.na(W9_Social_Other_di))

  # check it with the original dataset
  #filter_at(SocialMedia, c(2:(ncol(SocialMedia)-1)), all_vars(is.na(.)))

# People who answered this section
SocialMedia.count.noNA <- filter(SocialMedia.count, !(is.na(W9_Social_Facebook_di) & is.na(W9_Social_Instagram_di) & is.na(W9_Social_Twitter_di) & is.na(W9_Social_Linkedin_di) & is.na(W9_Social_Pinterest_di) & is.na(W9_Social_Snapchat_di) & is.na(W9_Social_Other_di)))

# People who answered all questions
SocialMedia.count.valid <- filter(SocialMedia.count, (!is.na(W9_Social_Facebook_di)) & (!is.na(W9_Social_Instagram_di)) & (!is.na(W9_Social_Twitter_di)) & (!is.na(W9_Social_Linkedin_di)) & (!is.na(W9_Social_Pinterest_di)) & (!is.na(W9_Social_Snapchat_di)) & (!is.na(W9_Social_Other_di)))

# filter_at(SocialMedia.count, c("W9_Social_Facebook_di", "W9_Social_Instagram_di", "W9_Social_Twitter_di", "W9_Social_Linkedin_di", "W9_Social_Pinterest_di", "W9_Social_Snapchat_di", "W9_Social_Other_di"), all_vars(!is.na(.)))

SocialMedia.count.noNA$count <- apply(SocialMedia.count.noNA[, -1], 1, sum)
```

For the question "How often do you visit the following social media sites?", `r nrow(SocialMedia.count.NA)` participants don't have any valid information on any item. `r nrow(SocialMedia.count.noNA)` participants have at least one valid information among 7 social media accounts. `r nrow(SocialMedia.count.valid)` participants have valid information on all 7 social media accounts for this question.

Among participants who have valid information on all 7 accounts, the count of social media account daily (i.e. "several times a day" or "daily") is summarized below:
```{r}
# frequency table
TableSocial <- rbind(table(SocialMedia.count.noNA$count), round(prop.table(table(SocialMedia.count.noNA$count))*100, 2))
rownames(TableSocial) <- c("Frequency", "Percentage")

# frequency table exclude zero
TableSocialNoZero <- rbind(table(SocialMedia.count.noNA[SocialMedia.count.noNA$count > 0, "count"]),
round(prop.table(table(SocialMedia.count.noNA[SocialMedia.count.noNA$count > 0, "count"]))*100, 2))
rownames(TableSocialNoZero) <- c("Frequency", "Percentage")

# frequency table: 0 vs. >= 1
SocialMedia.count.noNA <- mutate(SocialMedia.count.noNA, count.di = ifelse(count > 0, 1, 0))
TableSocialDi <- rbind(table(SocialMedia.count.noNA$count.di),
round(prop.table(table(SocialMedia.count.noNA$count.di))*100, 2))
rownames(TableSocialDi) <- c("Frequency", "Percentage")
colnames(TableSocialDi) <- c("0", "at least 1")

knitr::kable(TableSocial, caption = "Count of Social Media Sites")
knitr::kable(TableSocialNoZero, caption = "Count of Social Media Sites (exclude zero)")
knitr::kable(TableSocialDi, caption = "Count of Social Media Sites (0 vs. at least 1)")
```

Among participants who have at least one valid information among 7 accounts, assuming that missing items means "do not use it", the count of social media account daily (i.e. "several times a day" or "daily") is summarized below:
```{r}
SocialMedia.count.noNA$count.NA.Eq.Zero <- apply(SocialMedia.count.noNA[, c("W9_Social_Facebook_di", "W9_Social_Instagram_di", "W9_Social_Twitter_di", "W9_Social_Linkedin_di", "W9_Social_Pinterest_di", "W9_Social_Snapchat_di", "W9_Social_Other_di")], 1, sum, na.rm = T)

# frequency table
TableSocial.NA.Eq.Zero <- rbind(table(SocialMedia.count.noNA$count.NA.Eq.Zero),
round(prop.table(table(SocialMedia.count.noNA$count.NA.Eq.Zero))*100, 2))
rownames(TableSocial.NA.Eq.Zero) <- c("Frequency", "Percentage")

# frequency table exlude zero
TableSocial.NA.Eq.Zero.NoZero <- rbind(table(SocialMedia.count.noNA[SocialMedia.count.noNA$count.NA.Eq.Zero > 0, "count.NA.Eq.Zero"]),
round(prop.table(table(SocialMedia.count.noNA[SocialMedia.count.noNA$count.NA.Eq.Zero > 0, "count.NA.Eq.Zero"]))*100, 2))
rownames(TableSocial.NA.Eq.Zero.NoZero) <- c("Frequency", "Percentage")

# frequency table: 0 vs. >= 1
SocialMedia.count.noNA <- mutate(SocialMedia.count.noNA, count.NA.Eq.Zero.di = ifelse(count.NA.Eq.Zero > 0, 1, 0))
TableSocial.NA.Eq.Zero.di <- rbind(table(SocialMedia.count.noNA$count.NA.Eq.Zero.di),
round(prop.table(table(SocialMedia.count.noNA$count.NA.Eq.Zero.di))*100, 2))
rownames(TableSocial.NA.Eq.Zero.di) <- c("Frequency", "Percentage")
colnames(TableSocial.NA.Eq.Zero.di) <- c("0", "at least 1")

knitr::kable(TableSocial.NA.Eq.Zero, caption = "Count of Social Media Sites")
knitr::kable(TableSocial.NA.Eq.Zero.NoZero, caption = "Count of Social Media Sites (exclude zero)")
knitr::kable(TableSocial.NA.Eq.Zero.di, caption = "Count of Social Media Sites (0 vs. at least 1)")
```

## XX% have ever vaped e-cigarettes or cannabis
```{r}
EcigCannabis <- select(data, record_id, W9_Life_Use_Sub_3a, W9_Life_Use_Sub_31a, W9_Life_Use_Sub_27a)

  # check the coding
  # apply(EcigCannabis[, -1], 2, table)

EcigCannabis.NA <- filter_at(EcigCannabis, c(2:ncol(EcigCannabis)), all_vars(is.na(.)))

EcigCannabis.noNA <- filter_at(EcigCannabis, c(2:ncol(EcigCannabis)), any_vars(!is.na(.)))

EcigCannabis.valid <- filter_at(EcigCannabis, c(2:ncol(EcigCannabis)), all_vars(!is.na(.)))

EcigCannabis.noNA <- mutate(EcigCannabis.noNA, Ecig_3a_di = ifelse(W9_Life_Use_Sub_3a == 1, 0, 1), Ecig_31a_di = ifelse(W9_Life_Use_Sub_31a == 1, 0, 1), Ecig_27a_di = ifelse(W9_Life_Use_Sub_27a == 1, 0, 1))

EcigCannabis.noNA <- mutate(EcigCannabis.noNA, sum = Ecig_3a_di + Ecig_31a_di + Ecig_27a_di)

EcigCannabis.noNA <- mutate(EcigCannabis.noNA, EverOrNot = ifelse(sum == 0, 0, 1))
```

For the question "Have you ever used the following substances in your life?", `r nrow(EcigCannabis.NA)` participants don't have any valid information on [W9_Life_Use_Sub_3a], [W9_Life_Use_Sub_31a], or [W9_Life_Use_Sub_27a]. `r nrow(EcigCannabis.noNA)` participants have valid information on all three variables. 

Within participants who have valid information on all three variables, whether used these items are summarized below:

```{r}
TableEcigCannabis <- rbind(table(EcigCannabis.noNA$EverOrNot),
round(prop.table(table(EcigCannabis.noNA$EverOrNot))*100, 2))

rownames(TableEcigCannabis) <- c("Frequency", "Percentage")
colnames(TableEcigCannabis) <- c("Not Use", "Ever Use")

knitr::kable(TableEcigCannabis, caption = "ever vaped e-cigarettes or cannabis")
```

## XX% report regular drug use or a mental health issue
```{r}
DAST <- select(data, record_id, starts_with("W9_Dast"))
CESD <- select(data, record_id, starts_with("W9_Cesd"))
GAD <- select(data, record_id, starts_with("W9_Gad"))

DrugOrMental <- select(data, record_id, starts_with("W9_Dast"), starts_with("W9_Cesd"), starts_with("W9_Gad"))
  # check the coding
  # apply(DAST[, -1], 2, table)
  # apply(CESD[, -1], 2, table)
  # apply(GAD[, -1], 2, table)
#"W9_Dast_1", "W9_Dast_2", "W9_Dast_3", "W9_Dast_4", "W9_Dast_5", "W9_Dast_6", "W9_Dast_7", "W9_Dast_8", "W9_Dast_9", "W9_Dast_10", "W9_Cesd_10_1", "W9_Cesd_10_2", "W9_Cesd_10_3", "W9_Cesd_10_4", "W9_Cesd_10_5", "W9_Cesd_10_6", "W9_Cesd_10_7", "W9_Cesd_10_8", "W9_Cesd_10_9", "W9_Cesd_10_10"

DAST_exclude <- filter_at(DrugOrMental, c("W9_DAST_1", "W9_DAST_2", "W9_DAST_3", "W9_DAST_4", "W9_DAST_5", "W9_DAST_6", "W9_DAST_7", "W9_DAST_8", "W9_DAST_9", "W9_DAST_10"), all_vars(is.na(.)))

CESD_exclude <- filter_at(DrugOrMental, c("W9_CESD_10_1", "W9_CESD_10_2", "W9_CESD_10_3", "W9_CESD_10_4", "W9_CESD_10_5", "W9_CESD_10_6", "W9_CESD_10_7", "W9_CESD_10_8", "W9_CESD_10_9", "W9_CESD_10_10"), all_vars(is.na(.)))

GAD_exclude <- filter_at(DrugOrMental, c("W9_GAD_1", "W9_GAD_2", "W9_GAD_3", "W9_GAD_4", "W9_GAD_5", "W9_GAD_6", "W9_GAD_7"), all_vars(is.na(.)))

Exclude_id <- unique(c(DAST_exclude$record_id, CESD_exclude$record_id, GAD_exclude$record_id))

DrugOrMental.noNA <- filter(DrugOrMental, !(record_id %in% Exclude_id))

# DAST Scoring:
# Score 1 point for each question answered “Yes,” except for question 3 for which a “No” receives 1 point. Replace NA with 0 to calculate the sum score

DrugOrMental.noNA <- mutate(DrugOrMental.noNA, W9_DAST_3_score = ifelse(W9_DAST_3 == 1, 0, 1))

DrugOrMental.noNA$W9_DAST_sum_new <- apply(DrugOrMental.noNA[ , c("W9_DAST_1",  "W9_DAST_2", "W9_DAST_3_score", "W9_DAST_4", "W9_DAST_5", "W9_DAST_6", "W9_DAST_7", "W9_DAST_8", "W9_DAST_9", "W9_DAST_10")], 1, sum, na.rm = T)


# CESD Scoring:
# question 1 & 2: Rarely or none of the time = 3 ~ All of the time = 0; 
# Other questions: Rarely or none of the time = 0 ~ All of the time = 3;
# The total score is calculated by finding the sum of 10 items. Do not score the form if more than 2 items are missing. Any score equal to or above 10 is considered depressed.

DrugOrMental.noNA <- mutate(DrugOrMental.noNA, W9_CESD_10_1_new = 3 - W9_CESD_10_1, W9_CESD_10_2_new = 3 - W9_CESD_10_2)

SumNa <- function(varlist) {
  num.NA <- sum(is.na(varlist))
  return(num.NA)
}

DrugOrMental.noNA$W9_CESD.num.NA <- apply(DrugOrMental.noNA[, c("W9_CESD_10_1_new", "W9_CESD_10_2_new", "W9_CESD_10_3", "W9_CESD_10_4", "W9_CESD_10_5", "W9_CESD_10_6", "W9_CESD_10_7", "W9_CESD_10_8", "W9_CESD_10_9", "W9_CESD_10_10")], 1, SumNa)

# table(DrugOrMental.noNA$W9_CESD.num.NA)
# No one has more than 2 items missing, so no need to exclude the participants again

DrugOrMental.noNA$W9_CESD_10_sum_new <- apply(DrugOrMental.noNA[, c("W9_CESD_10_1_new", "W9_CESD_10_2_new", "W9_CESD_10_3", "W9_CESD_10_4", "W9_CESD_10_5", "W9_CESD_10_6", "W9_CESD_10_7", "W9_CESD_10_8", "W9_CESD_10_9", "W9_CESD_10_10")], 1, sum, na.rm = T)


# GAD Scoring:
# sum score is calculated by the questions coded as 0 -3

DrugOrMental.noNA <- mutate(DrugOrMental.noNA, W9_GAD_1_new = W9_GAD_1 - 1, W9_GAD_2_new = W9_GAD_2 - 1, W9_GAD_3_new = W9_GAD_3 - 1, W9_GAD_4_new = W9_GAD_4 - 1, W9_GAD_5_new = W9_GAD_5 - 1, W9_GAD_6_new = W9_GAD_6 - 1, W9_GAD_7_new = W9_GAD_7 - 1)

DrugOrMental.noNA$W9_GAD_sum_new <- apply(DrugOrMental.noNA[, c("W9_GAD_1_new", "W9_GAD_2_new", "W9_GAD_3_new", "W9_GAD_4_new", "W9_GAD_5_new", "W9_GAD_6_new", "W9_GAD_7_new")], 1, sum, na.rm = T)

# write.csv(DrugOrMental.noNA, file = "/Users/zhan039/Desktop/USC_HEAL/HH/04072020/test_new.csv")

```

`r length(Exclude_id)` participants who have all missing items for at least one test (Drug Abuse Screening Test [DAST-10], Depression Scale [CESD-R], Anxiety Scale [GAD-7]) are excluded from the analysis below. `r nrow(DrugOrMental.noNA)` participants who have valid information on all three tests are included in the analysis below.

In terms of DAST-10, the sum score is calculated by the sum of 10 items (Score 1 point for each question answered “Yes,” except for question 3 for which a “No” receives 1
point). Missing items are scored as zero to calculate the sum score.

In terms of CESD-R, the sum score is calculated by the sum of 10 items. No participant has more than two missing items. All missing items are scored as zero to calculate the sum score.

In terms of GAD-7, the sum score is calculated by the sum of 7 itmes (coded as 0-3). Missing items are scored as zero to calculate the sum score.

(Please let me know if you hope to calculate sum scores in a different way, like only include participants who have valid information on all items for each test. I noticed that the dataset contains some sum scores for DAST-10 and CESD-R, but DAST-10 sum score looks calculated in a different way from the manual's you sent me. Just let me know if you hope to use the existing sum scores, and I'm glad to update the analysis.)

Within participants who have valid information on all three tests, people who report regular drug use (DAST-10 sum score > 2) or a mental health issue (CESD-R sum score >= 10 or GAD-7 sum score > 10) are summarized below:
```{r}
DrugOrMental.noNA<- mutate(DrugOrMental.noNA, DrugOrMental = ifelse((W9_DAST_sum_new > 2 | W9_CESD_10_sum_new >= 10 | W9_GAD_sum_new > 10), 1, 0))

TableDrugMental <- rbind(table(DrugOrMental.noNA$DrugOrMental),
round(prop.table(table(DrugOrMental.noNA$DrugOrMental))*100, 2))
rownames(TableDrugMental) <- c("Frequency", "Percentage")
colnames(TableDrugMental) <- c("No Drug Use nor Mental Health Issue", "Drug Use or Mental Health Issue")

knitr::kable(TableDrugMental, caption = "Report Regular Drug Use or a Mentlal Health Issue")
```


```{r include=FALSE}
#Within participants who have at least one valid sum score, assuming that the invalid sum score means the participant don't have any issue in that test, people who report regular drug use (DAST-10 sum score > 2) or a mental health issue (CESD-R sum score >= 10 or GAD-7 sum score > 10) are summarized below:

DrugOrMental.noNA <- mutate(DrugOrMental.noNA, DrugOrMental = ifelse((W9_DAST_sum_new > 2 | W9_CESD_10_sum_new >= 10 | W9_GAD_sum_new > 10), 1, 0))

DrugOrMental.noNA <- mutate(DrugOrMental.noNA, DrugOrMental = ifelse(is.na(DrugOrMental), 0, DrugOrMental))

TableDrugMental.NA.Eq.Zero <- rbind(table(DrugOrMental.noNA$DrugOrMental),
round(prop.table(table(DrugOrMental.noNA$DrugOrMental))*100, 2))
rownames(TableDrugMental.NA.Eq.Zero) <- c("Frequency", "Percentage")
colnames(TableDrugMental.NA.Eq.Zero) <- c("No Drug Use nor Mental Health Issue", "Drug Use or Mental Health Issue")

knitr::kable(TableDrugMental.NA.Eq.Zero, caption = "Report Regular Drug Use or a Mentlal Health Issue")
```


