---
title: "Pilot 1 - TP/MTurk Self Launch - Distribution of Survey Time"
author: "Yi"
date: "5/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(kableExtra)
library(ggplot2)
```

```{r}
data <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04292020/TPMT.csv", na.strings = "")
```

## Redcap Survey Time

```{r}
# create the redcap survey time
CreateRCtime <- function(platform) {
  time.ncol <- ends_with("timestamp", vars = colnames(platform))
  start <- time.ncol[1]
  end <- time.ncol[length(time.ncol)]

  platform$start.time <- strptime(platform[, start], format = "%Y-%m-%d %H:%M:%S") 
  platform$end.time <- strptime(platform[, end], format = "%Y-%m-%d %H:%M:%S")

  platform$diff.time <- difftime(platform$end.time, platform$start.time, units = "secs")
  platform$diff.time <- as.numeric(platform$diff.time)
  
  return(platform)
}

data <- CreateRCtime(data)
```

Among all participants in the Redcap (N = 159), 151 participants have valid Redcap survey time (from the beginning of "Work ID" section to the beginning of "Advertisements" section), and they distribute as below:
```{r}
# sum(!is.na(data$diff.time))
RC.mean <- mean(data$diff.time, na.rm = T)

ggplot(data = data, aes( x = redcapid, y = diff.time)) + geom_point(na.rm = T) + labs(y = "Redcap Survey Time (in secs)", title = "Pilot 1 - TP/MTurk Self Launch Redcap Survey Time")
```

It looks good. Then add the reference lines:
```{r}
clean.data <- data
RC.clean.mean <- mean(clean.data$diff.time, na.rm = T)
RC.under.mean <- clean.data[clean.data$diff.time < RC.clean.mean, ] # TRUE + NA
RC.under.mean.5pct <- quantile(RC.under.mean$diff.time, probs = 0.05, na.rm = T)
RC.clean.sd <- sd(clean.data$diff.time, na.rm = T)
RC.clean.mean.sd <- RC.clean.mean - 2 * RC.clean.sd

ggplot(data = clean.data, aes( x = redcapid, y = diff.time)) + 
  geom_point(na.rm = T) + 
  labs(y = "Redcap Survey Time (in secs)", title = "Pilot 1 - TP/MTurk Self Launch Redcap Survey Time") + 
  geom_hline(aes(yintercept = RC.clean.mean, colour = "Mean"), linetype = "dashed") + 
  geom_hline(aes(yintercept = RC.under.mean.5pct, colour = str_wrap("Under the Mean, bottom 5% of the Redcap Survey Time ", width = 20)), linetype = "dashed") +
  geom_hline(aes(yintercept = RC.clean.mean.sd, colour = "Mean - 2SD"), linetype = "dashed") + 
  theme(legend.key.height = unit(1, "cm")) + 
  scale_colour_discrete(name = "Reference Lines",
                        breaks = c("Mean", str_wrap("Under the Mean, bottom 5% of the Redcap Survey Time ", width = 20), "Mean - 2SD"),
                        labels = c("Mean", str_wrap("Under the Mean, bottom 5% of the Redcap Survey Time ", width = 20), "Mean - 2SD"))
```

Under the mean survey time from the Redcap dataset, the bottom 5% of the survey time are listed below:
```{r}
RC.5pct.outliers <- clean.data[which(clean.data$diff.time < RC.under.mean.5pct), c("redcapid", "diff.time")]
colnames(RC.5pct.outliers)[2] <- "Redcap Survey Time"
rownames(RC.5pct.outliers) <- NULL

kableExtra::kable(RC.5pct.outliers, caption = "Potential Questionable Redcap Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F)
```

## Sawtooth Survey Time

```{r}
bot <- readRDS("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04232020/MaxDiff_Pilot1_BotFit.rds")

mergedata <- left_join(clean.data, bot, by = "redcapid")

# sum(!is.na(mergedata$md_time_inSec))
```

After merging the Redcap dataset and the Sawtooth dataset by redcapid, among all participants in the merged dataset (N = 159), 150 participants have valid information on Sawtooth survey time, and they distribute as below:
```{r}
ggplot(data = mergedata, aes(x = redcapid, y = md_time_inSec)) + 
  geom_point(na.rm = T) +
  labs(y = "Sawtooth Survey Time (in secs)", title = "Pilot 1 - TP/MTurk Self Launch Sawtooth Survey Time") 
```

It looks good. Then add the referece lines:
```{r}
ST.mean <- mean(mergedata$md_time_inSec, na.rm = T)
ST.sd <- sd(mergedata$md_time_inSec, na.rm = T)
ST.under.mean <- mergedata[mergedata$md_time_inSec < ST.mean, ]
ST.under.mean.5pct <- quantile(ST.under.mean$md_time_inSec, probs = 0.05, na.rm = T)
ST.mean.sd <- ST.mean - 2 * ST.sd

ggplot(data = mergedata, aes(x = redcapid, y = md_time_inSec)) + 
  geom_point(na.rm = T) +
  labs(y = "Sawtooth Survey Time (in secs)", title = "Pilot 1 - TP/MTurk Self Launch Sawtooth Survey Time") +
  geom_hline(aes(yintercept = ST.mean, colour = "Mean"), linetype = "dashed") +
  geom_hline(aes(yintercept = ST.under.mean.5pct, colour = str_wrap("Under the Mean, bottom 5% of the Redcap Survey Time ", width = 20)), linetype = "dashed") +
  geom_hline(aes(yintercept = ST.mean.sd, colour = "Mean - 2SD"), linetype = "dashed") + 
  theme(legend.key.height = unit(1, "cm")) + 
  scale_colour_discrete(name = "Reference Lines",
                        breaks = c("Mean", str_wrap("Under the Mean, bottom 5% of the Redcap Survey Time ", width = 20), "Mean - 2SD"),
                        labels = c("Mean", str_wrap("Under the Mean, bottom 5% of the Redcap Survey Time ", width = 20), "Mean - 2SD"))
```

Under the mean survey time from the merged dataset, the bottom 5% of the survey time are listed below:
```{r}
ST.5pct.outliers <- mergedata[which(mergedata$md_time_inSec < ST.under.mean.5pct), c("redcapid", "md_time_inSec")]
colnames(ST.5pct.outliers)[2] <- "Sawtooth Survey Time"
rownames(ST.5pct.outliers) <- NULL

kableExtra::kable(ST.5pct.outliers, caption = "Potential Questionable Sawtooth Survey Time", align = "c") %>% kable_styling(bootstrap_options = "striped", full_width = F)
```

