---
title: "Pilot 1 - All Platforms"
author: "Yi"
date: "4/29/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(descr)
library(pander)
panderOptions("round", 1)
```

```{r}
Prolific <- read.csv('/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04292020/Prolific.csv')
MTself <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04292020/MTself.csv")
TPMT <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04292020/TPMT.csv")
MTconc <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04292020/MTconc.csv")
PP <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04292020/PP.csv")

bot <- readRDS("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04232020/MaxDiff_Pilot1_BotFit.rds")
```


```{r}
# create the redcap survey time
CreateRCtime <- function(platform) {
  time.ncol <- ends_with("timestamp", vars = colnames(platform))
  start <- time.ncol[1]
  end <- time.ncol[length(time.ncol)]

  platform$start.time <- strptime(platform[, start], format = "%Y-%m-%d %H:%M:%S") 
  platform$end.time <- strptime(platform[, end], format = "%Y-%m-%d %H:%M:%S")

  platform$diff.time <- difftime(platform$end.time, platform$start.time, units = "secs")
  platform$diff.time <- as.numeric(platform$diff.time)
  
  return(platform)
}

Prolific <- CreateRCtime(Prolific)
MTself <- CreateRCtime(MTself)
TPMT <- CreateRCtime(TPMT)
MTconc <- CreateRCtime(MTconc)
PP <- CreateRCtime(PP)
```


```{r}
Prolific.att.RC <- select(Prolific, redcapid, att_check1___1, att_check1___2, att_check1___3, att_check1___4, att_check1___5, last_30_ecig_yn, att_check2, att_check3a, att_check3b, diff.time)

MTself.att.RC <- select(MTself, redcapid, att_check1___1, att_check1___2, att_check1___3, att_check1___4, att_check1___5, last_30_ecig_yn, att_check2, att_check3a, att_check3b, diff.time)

TPMT.att.RC <- select(TPMT, redcapid, att_check1___1, att_check1___2, att_check1___3, att_check1___4, att_check1___5, last_30_ecig_yn, att_check2, att_check3a, att_check3b, diff.time)

MTconc.att.RC <- select(MTconc, redcapid, att_check1___1, att_check1___2, att_check1___3, att_check1___4, att_check1___5, last_30_ecig_yn, att_check2, att_check3a, att_check3b, diff.time)

PP.att.RC <- select(PP, redcapid, att_check1___1, att_check1___2, att_check1___3, att_check1___4, att_check1___5, last_30_ecig_yn, att_check2, att_check3a, att_check3b, diff.time)

data <- rbind(Prolific.att.RC, MTself.att.RC, TPMT.att.RC, MTconc.att.RC, PP.att.RC)
# length(data$redcapid)
```

```{r}
# result of each attention check question
data <- mutate(data, att1.success = ifelse(data$att_check1___1 == 1 & data$att_check1___4 == 1 & data$att_check1___5 == 1, 1, 0))

data <- mutate(data, att2.success = ifelse(data$last_30_ecig_yn == 1 & data$att_check2 == 3, 1, ifelse(data$last_30_ecig_yn == 1, 0, NA))) # people who are not asked the second question are marked as NA

data <- mutate(data, att3.success = ifelse(data$att_check3a == 4 & grepl("decision making", data$att_check3b, ignore.case = T), 1, 0))

data$att2.replaceNA <- data$att2.success
data$att2.replaceNA[is.na(data$att2.replaceNA)] <- 1 # people who are not asked are marked as success

data$sum.att.success <- apply(data[, c("att1.success", "att2.replaceNA", "att3.success")], 1, sum)

data$sum.att.failure <- 3 - data$sum.att.success

data$att1.success <- factor(data$att1.success, levels = c(0, 1), labels = c("fail", "success"))
data$att2.replaceNA <- factor(data$att2.replaceNA, levels = c(0, 1), labels = c("fail", "success"))
data$att3.success <- factor(data$att3.success, levels = c(0,1), labels = c("fail", "success"))
```

```{r}
Freq <- as.data.frame(matrix(table(data$sum.att.failure)))
Perc <- as.data.frame(matrix(prop.table(table(data$sum.att.failure)) * 100)) 
table.count.failure <- cbind(Freq, Perc)

table.count.failure[5, ] <- c(sum(table.count.failure[, 1]), sum(table.count.failure[, 2]))

rownames(table.count.failure) <- c(0, 1, 2, 3, "Total")
colnames(table.count.failure) <- c("Frequency", "Percentage (%)")

knitr::kable(table.count.failure, digits = 1, caption = "Number of Attention Check Failed")
```

1) A cross tab of number of attention checks failed (0-3) by bot status
```{r, include=FALSE}
count <- select(data, redcapid, sum.att.failure)

pilot1 <- left_join(count, bot, by = "redcapid")

table(pilot1$sum.att.failure, pilot1$md_fit_cut)

pander:: pander(descr::CrossTable(pilot1$sum.att.failure, pilot1$md_fit_cut, prop.chisq = FALSE, dnn = c("Number of Attention Check Failures", "Bot Status")), caption = "Number of Attention Check Failures X Bot Status", digits = panderOptions("round"))
```

---------------------------------------------------------------
          &nbsp;\            Bot Status\   &nbsp;\    &nbsp;\  
 Number of Attention Check        0           1        Total   
         Failures                                              
--------------------------- ------------- ---------- ----------
          **0**\              &nbsp;\      &nbsp;\    &nbsp;\  
            N\                 544\         62\        606\    
         Row(%)\              89.8%\       10.2%\     74.8%\   
        Column(%)\            79.4%\       49.6%\        \     
         Total(%)               67.2%        7.7%              

          **1**\              &nbsp;\      &nbsp;\    &nbsp;\  
            N\                 123\         34\        157\    
         Row(%)\              78.3%\       21.7%\     19.4%\   
        Column(%)\            18.0%\       27.2%\        \     
         Total(%)               15.2%        4.2%              

          **2**\              &nbsp;\      &nbsp;\    &nbsp;\  
            N\                  12\         15\        27\     
         Row(%)\              44.4%\       55.6%\     3.3%\    
        Column(%)\             1.8%\       12.0%\        \     
         Total(%)               1.5%         1.9%              

          **3**\              &nbsp;\      &nbsp;\    &nbsp;\  
            N\                  6\          14\        20\     
         Row(%)\              30.0%\       70.0%\     2.5%\    
        Column(%)\             0.9%\       11.2%\        \     
         Total(%)               0.7%         1.7%              

          Total\                685\        125\        810\   
                                84.6%       15.4%              
---------------------------------------------------------------

Table: Number of Attention Check Failures $\times$ Bot Status

2) A cross tab of each attention check (failed vs. did not fail) by bot status 
```{r, include=FALSE}
each.failure <- select(data, redcapid, att1.success, att2.replaceNA, att3.success)

pilot1.each <- left_join(each.failure, bot, by = "redcapid")

pander:: pander(descr::CrossTable(pilot1.each$att1.success, pilot1.each$md_fit_cut, prop.chisq = FALSE, dnn = c("First Attention Check", "Bot Status")), caption = "First Attention Check X Bot Status", digits = panderOptions("round"))
```

-----------------------------------------------------------
        &nbsp;\          Bot Status\   &nbsp;\    &nbsp;\  
 First Attention Check        0           1        Total   
----------------------- ------------- ---------- ----------
      **fail**\           &nbsp;\      &nbsp;\    &nbsp;\  
          N\               123\         45\        168\    
       Row(%)\            73.2%\       26.8%\     20.7%\   
      Column(%)\           18%\         36%\         \     
       Total(%)             15.2%        5.6%              

     **success**\         &nbsp;\      &nbsp;\    &nbsp;\  
          N\               562\         80\        642\    
       Row(%)\            87.5%\       12.5%\     79.3%\   
      Column(%)\           82%\         64%\         \     
       Total(%)             69.4%        9.9%              

        Total\              685\        125\        810\   
                            84.6%       15.4%              
-----------------------------------------------------------

Table: First Attention Check $\times$ Bot Status

```{r, include=FALSE}
pander:: pander(descr::CrossTable(pilot1.each$att2.replaceNA, pilot1.each$md_fit_cut, prop.chisq = FALSE, dnn = c("Second Attention Check", "Bot Status")), caption = "Second Attention Check X Bot Status", digits = panderOptions("round"))
```

------------------------------------------------------------
        &nbsp;\           Bot Status\   &nbsp;\    &nbsp;\  
 Second Attention Check        0           1        Total   
------------------------ ------------- ---------- ----------
       **fail**\           &nbsp;\      &nbsp;\    &nbsp;\  
          N\                 21\         29\        50\     
        Row(%)\            42.0%\       58.0%\     6.2%\    
      Column(%)\            3.1%\       23.2%\        \     
        Total(%)             2.6%         3.6%              

     **success**\          &nbsp;\      &nbsp;\    &nbsp;\  
          N\                664\         96\        760\    
        Row(%)\            87.4%\       12.6%\     93.8%\   
      Column(%)\           96.9%\       76.8%\        \     
        Total(%)             82.0%       11.9%              

         Total\              685\        125\        810\   
                             84.6%       15.4%              
------------------------------------------------------------

Table: Second Attention Check $\times$ Bot Status

```{r, include=FALSE}
pander:: pander(descr::CrossTable(pilot1.each$att3.success, pilot1.each$md_fit_cut, prop.chisq = FALSE, dnn = c("Third Attention Check", "Bot Status")), caption = "Third Attention Check X Bot Status", digits = panderOptions("round"))
```

-----------------------------------------------------------
        &nbsp;\          Bot Status\   &nbsp;\    &nbsp;\  
 Third Attention Check        0           1        Total   
----------------------- ------------- ---------- ----------
      **fail**\           &nbsp;\      &nbsp;\    &nbsp;\  
          N\                21\         32\        53\     
       Row(%)\            39.6%\       60.4%\     6.5%\    
      Column(%)\           3.1%\       25.6%\        \     
       Total(%)             2.6%         4.0%              

     **success**\         &nbsp;\      &nbsp;\    &nbsp;\  
          N\               664\         93\        757\    
       Row(%)\            87.7%\       12.3%\     93.5%\   
      Column(%)\          96.9%\       74.4%\        \     
       Total(%)             82.0%       11.5%              

        Total\              685\        125\        810\   
                            84.6%       15.4%              
-----------------------------------------------------------

Table: Third Attention Check $\times$ Bot Status

3) Mean sawtooth survey complete time by bot status
```{r}
Mdtime.bot <- pilot1 %>% group_by(md_fit_cut) %>% summarise(mean(md_time_inSec, na.rm = T), N = sum(!is.na(md_time_inSec)))
# Mdtime.bot <- Mdtime.bot[-3, ]
colnames(Mdtime.bot) <- c("Bot Status", "Mean", "N")
knitr::kable(Mdtime.bot, digits = 2, caption = "Mean Sawtooth Survey Complete Time (seconds)")
```

4) Mean sawtooth survey complete time by number of attention checks failed
```{r}
Mdtime.sum.fail <- pilot1 %>% group_by(sum.att.failure) %>% summarise(mean(md_time_inSec, na.rm = T), N = sum(!is.na(md_time_inSec)))
colnames(Mdtime.sum.fail) <- c("Number of Attetion Check Failure", "Mean", "Valid N")
knitr::kable(Mdtime.sum.fail, digits = 2, caption = "Mean Sawtooth Survey Complete Time (seconds)")
```

5) Mean redcap survey complete time by bot status
(Redcap survey time is the time from the beginning of the "Worker ID" section to the beginning of the "Advertisement" section.)
```{r}
RCtime <- select(data, redcapid, diff.time)

RCtime.bot.data <- left_join(RCtime, bot, by = "redcapid")

RCtime.bot <- RCtime.bot.data %>% group_by(md_fit_cut) %>% summarise(mean(diff.time, na.rm = T), N = sum(!is.na(diff.time)))

colnames(RCtime.bot) <- c("Bot Status", "Mean", "N")

knitr::kable(RCtime.bot, digits = 2, caption = "Mean Redcap Survey Complete Time (seconds)")
```

6) Mean redcap survey complete time by number of attention checks failed
(Redcap survey time is the time from the beginning of the "Worker ID" section to the beginning of the "Advertisement" section.)
```{r}
RCtime.att.data <- select(data, redcapid, diff.time, sum.att.failure)

RCtime.sum.fail <- RCtime.att.data %>% group_by(sum.att.failure) %>% summarise(mean(diff.time, na.rm = T), N = sum(!is.na(diff.time)))

colnames(RCtime.sum.fail) <- c("Number of Attetion Check Failure", "Mean", "Valid N")
knitr::kable(RCtime.sum.fail, digits = 2, caption = "Mean Redcap Survey Complete Time (seconds)")
```

