---
title: "Smoking Type in Prescreen X Smoking History in Redcap"
author: "Yi"
date: "9/16/2020"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE)
```

```{r}
library(tidyverse)
library(gmodels)
library(pander)
```

```{r}
pilot2 <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/Christie/Prolific Pilot 2 Ppt Smoking Status.csv", stringsAsFactors = F)
pilot3_1 <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/Christie/Prolific Pilot 3 (wave 1) Smoking Status.csv", stringsAsFactors = F)
pilot3_2 <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/Christie/Prolific Pilot 3 (wave 2) Smoking Status.csv", stringsAsFactors = F)

data_pilot2_3 <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/Final_Data/EVOC_pilot2_3/EVOC_pilot2_3_09152020.csv")
data_pilot2_3 <- data_pilot2_3[, -1]
```

```{r prepare prescreener data}
length(unique(pilot2$participant_id))
length(unique(pilot3_2$participant_id))
length(intersect(unique(pilot2$participant_id), unique(pilot3_2$participant_id)))

pilot2_type <- pilot2[, c("participant_id", "Smoking..Tobacco.or.e.cigarettes")]
pilot2_type$pilot <- 2

pilot3_2_type <- pilot3_2[, c("participant_id", "Smoking..Tobacco.or.e.cigarettes")]
pilot3_2_type$pilot <- 3

data_type <- rbind(pilot2_type, pilot3_2_type)

data <- merge(data_pilot2_3, data_type, by.x = c("prolificpid", "pilot"), by.y = c("participant_id", "pilot"), all.x = T)
```

```{r}
# Ever use: 0 No, 1 Yes but not in the last 6 months, 2 Yes in the last 6 months but not in the last 30 days, 3 Yes in the last 30 days, 9 Yes in the last 6 months but don't know whether 30 days

EverUse <- function(var.ever, var.30.last){
  temp.data <- mutate(data, temp_ever_use_new = ifelse(get(var.ever) %in% 0, 0,
                                                   ifelse(get(var.ever) %in% 1, 1,
                                                          ifelse(get(var.ever) %in% 2 & get(var.30.last) %in% 0, 2,
                                                                 ifelse(get(var.ever) %in% 2 & get(var.30.last) %in% 1, 3, 
                                                                        ifelse(get(var.ever) %in% 2 & get(var.30.last) %in% 9, 9, NA))))))
  
}

```

```{r}
# disposal
ever_disp <- EverUse("ever_disp", "last_30_ecig_dispose")
data <- rename(ever_disp, "ever_disp_new" = temp_ever_use_new)
select(data, redcapid, ever_disp, last_30_ecig_dispose, ever_disp_new)

# vape pen
ever_pen <- EverUse("ever_pen", "last_30_ecig_pen")
data <- rename(ever_pen, "ever_pen_new" = temp_ever_use_new)

# Mod
ever_mod <- EverUse("ever_mod", "last_30_ecig_mod")
data <- rename(ever_mod, "ever_mod_new" = temp_ever_use_new)

# Box Mod
ever_box_mod <- EverUse("ever_box_mod", "last_30_ecig_box_mod")
data <- rename(ever_box_mod, "ever_box_mod_new" = temp_ever_use_new)

# JUUL
ever_juul <- EverUse("ever_juul", "last_30_ecig_juul")
data <- rename(ever_juul, "ever_juul_new" = temp_ever_use_new)

# Other pod
ever_pod <- EverUse("ever_pod", "last_30_ecig_pod")
data <- rename(ever_pod, "ever_pod_new" = temp_ever_use_new)

# Smoking type in the presreen data
table(data$Smoking..Tobacco.or.e.cigarettes, useNA = "always")
class(data$Smoking..Tobacco.or.e.cigarettes)

data$Smoking_Type <- factor(data$Smoking..Tobacco.or.e.cigarettes, levels = sort(unique(data$Smoking..Tobacco.or.e.cigarettes)), labels = c(0:3))
```

**Ever_XXX_new:**
<br>0: No
<br>1: Yes, but not in the last 6 months 
<br>2: Yes, in the last 6 months but not in the last 30 days 
<br>3: Yes, in the last 30 days 
<br>9: Yes, in the last 6 months but don't know whether in the last 30 days

**Smoking Type in Prescreen:**
<br>0: Do not use e-cigarettes or tobacco products
<br>1: Only ever used e-cigarettes regularly (not tobacco products)
<br>2: Previously smoked tobacco products. Now only use e-cigarettes
<br>3: Regularly use both tobacco products and e-cigarettes         

```{r include=TRUE}

Tables <- function(varname){
  
pander(descr::CrossTable(data[, varname], data[, "Smoking_Type"], prop.r = T, prop.c = T, prop.t = F, prop.chisq = F, format = "SAS", dnn = c(varname, "Smoking Type in Prescreen")), digits = 1, split.table = Inf)

}

varlist <- data %>% select(., starts_with("ever") & ends_with("new")) %>% colnames()
pander(sapply(varlist, Tables))
```

