---
title: "Pilot1"
author: "Yi"
date: "4/23/2020"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(gmodels)
library(pander)
panderOptions("round", 1)
```


```{r, include=FALSE}
# load the dataset
data <- read.csv('/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04232020/ConjointAnalysisProl_DATA_2020-04-23_1502.csv')
```

```{r}
# explore attention check questions

 # table(data$att_check1___1, useNA = "always")
 # table(data$att_check1___2, useNA = "always")
 # table(data$att_check1___3, useNA = "always")
 # table(data$att_check1___4, useNA = "always")
 # table(data$att_check1___5, useNA = "always")
 # table(data$att_check2, useNA = "always")
 # table(data$last_30_ecig_yn, useNA = "always")

 # table(data$att_check3a, useNA = "always")
 # table(data$att_check3b, useNA = "always")

# result of each attention check question
data <- mutate(data, att1.success = ifelse(data$att_check1___1 == 1 & data$att_check1___4 == 1 & data$att_check1___5 == 1, 1, 0))

data <- mutate(data, att2.success = ifelse(data$last_30_ecig_yn == 1 & data$att_check2 == 3, 1, ifelse(data$last_30_ecig_yn == 1, 0, NA))) # people who are not asked the second question are marked as NA

data <- mutate(data, att3.success = ifelse(data$att_check3a == 4 & grepl("decision making", data$att_check3b, ignore.case = T), 1, 0))

# table(data$att2.success, useNA = "always")
data$att2.replaceNA <- data$att2.success
data$att2.replaceNA[is.na(data$att2.replaceNA)] <- 1 # people who are not asked are marked as success
# table(data$att2.replaceNA, useNA = "always")

data$sum.att.success <- apply(data[, c("att1.success", "att2.replaceNA", "att3.success")], 1, sum)

data$sum.att.failure <- 3 - data$sum.att.success

data$att1.success <- factor(data$att1.success, levels = c(0, 1), labels = c("fail", "success"))
data$att2.replaceNA <- factor(data$att2.replaceNA, levels = c(0, 1), labels = c("fail", "success"))
data$att3.success <- factor(data$att3.success, levels = c(0,1), labels = c("fail", "success"))
```

```{r}
Freq <- as.data.frame(matrix(table(data$sum.att.failure)))
Perc <- as.data.frame(matrix(prop.table(table(data$sum.att.failure)) * 100)) 
table.count.failure <- cbind(Freq, Perc)
table.count.failure <- rbind(table.count.failure, c(0, 0))

table.count.failure[5, ] <- c(sum(table.count.failure[, 1]), sum(table.count.failure[, 2]))
rownames(table.count.failure) <- c(0, 1, 2, 3, "Total")
colnames(table.count.failure) <- c("Frequency", "Percentage (%)")

knitr::kable(table.count.failure, digits = 1, caption = "Number of Attention Check Failed")
```

1) A cross tab of number of attention checks failed (0-3) by bot status

```{r, include=FALSE}

bot <- readRDS("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04232020/MaxDiff_Pilot1_BotFit.rds")

count <- select(data, redcapid, sum.att.failure)

pilot1 <- left_join(count, bot, by = "redcapid")

table(pilot1$sum.att.failure, pilot1$md_fit_cut)

pander:: pander(descr::CrossTable(pilot1$sum.att.failure, pilot1$md_fit_cut, prop.chisq = FALSE, dnn = c("Number of Attention Check Failures", "Bot Status")), caption = "Number of Attention Check Failures X Bot Status", digits = panderOptions("round"))

```

----------------------------------------------------------------
          &nbsp;\            Bot Status\    &nbsp;\    &nbsp;\  
 Number of Attention Check        0            1        Total   
         Failures                                               
--------------------------- ------------- ----------- ----------
          **0**\              &nbsp;\      &nbsp;\     &nbsp;\  
            N\                 113\          12\        125\    
         Row(%)\              90.4%\        9.6%\      83.3%\   
        Column(%)\            83.7%\       80.0%\         \     
         Total(%)               75.3%        8.0%               

          **1**\              &nbsp;\      &nbsp;\     &nbsp;\  
            N\                  22\          2\         24\     
         Row(%)\              91.7%\        8.3%\      16.0%\   
        Column(%)\            16.3%\       13.3%\         \     
         Total(%)               14.7%        1.3%               

          **2**\              &nbsp;\      &nbsp;\     &nbsp;\  
            N\                  0\           1\          1\     
         Row(%)\               0.0%\       100.0%\     0.7%\    
        Column(%)\             0.0%\        6.7%\         \     
         Total(%)               0.0%         0.7%               

          Total\                135\         15\         150\   
                                 90%          10%               
----------------------------------------------------------------

Table: Number of Attention Check Failures $\times$ Bot Status

2) A cross tab of each attention check (failed vs. did not fail) by bot status 
```{r, include=FALSE}
each.failure <- select(data, redcapid, att1.success, att2.replaceNA, att3.success)

pilot1.each <- left_join(each.failure, bot, by = "redcapid")

pander:: pander(descr::CrossTable(pilot1.each$att1.success, pilot1.each$md_fit_cut, prop.chisq = FALSE, dnn = c("First Attention Check", "Bot Status")), caption = "First Attention Check X Bot Status", digits = panderOptions("round"))
```

-----------------------------------------------------------
        &nbsp;\          Bot Status\   &nbsp;\    &nbsp;\  
 First Attention Check        0           1        Total   
----------------------- ------------- ---------- ----------
      **fail**\           &nbsp;\      &nbsp;\    &nbsp;\  
          N\                19\          2\        21\     
       Row(%)\            90.5%\       9.5%\      14.0%\   
      Column(%)\          14.1%\       13.3%\        \     
       Total(%)             12.7%        1.3%              

     **success**\         &nbsp;\      &nbsp;\    &nbsp;\  
          N\               116\         13\        129\    
       Row(%)\            89.9%\       10.1%\     86.0%\   
      Column(%)\          85.9%\       86.7%\        \     
       Total(%)             77.3%        8.7%              

        Total\              135\         15\        150\   
                             90%         10%               
-----------------------------------------------------------

Table: First Attention Check $\times$ Bot Status


```{r, include=FALSE}
pander:: pander(descr::CrossTable(pilot1.each$att2.replaceNA, pilot1.each$md_fit_cut, prop.chisq = FALSE, dnn = c("Second Attention Check", "Bot Status")), caption = "Second Attention Check X Bot Status", digits = panderOptions("round"))
```

-------------------------------------------------------------
        &nbsp;\           Bot Status\    &nbsp;\    &nbsp;\  
 Second Attention Check        0            1        Total   
------------------------ ------------- ----------- ----------
       **fail**\           &nbsp;\      &nbsp;\     &nbsp;\  
          N\                 2\           0\          2\     
        Row(%)\            100.0%\       0.0%\      1.3%\    
      Column(%)\            1.5%\        0.0%\         \     
        Total(%)             1.3%         0.0%               

     **success**\          &nbsp;\      &nbsp;\     &nbsp;\  
          N\                133\          15\        148\    
        Row(%)\            89.9%\       10.1%\      98.7%\   
      Column(%)\           98.5%\       100.0%\        \     
        Total(%)             88.7%        10.0%              

         Total\              135\         15\         150\   
                              90%          10%               
-------------------------------------------------------------

Table: Second Attention Check $\times$ Bot Status

```{r, include=FALSE}
pander:: pander(descr::CrossTable(pilot1.each$att3.success, pilot1.each$md_fit_cut, prop.chisq = FALSE, dnn = c("Third Attention Check", "Bot Status")), caption = "Third Attention Check X Bot Status", digits = panderOptions("round"))
```
 
-----------------------------------------------------------
        &nbsp;\          Bot Status\   &nbsp;\    &nbsp;\  
 Third Attention Check        0           1        Total   
----------------------- ------------- ---------- ----------
      **fail**\           &nbsp;\      &nbsp;\    &nbsp;\  
          N\                1\           2\         3\     
       Row(%)\            33.3%\       66.7%\     2.0%\    
      Column(%)\           0.7%\       13.3%\        \     
       Total(%)             0.7%         1.3%              

     **success**\         &nbsp;\      &nbsp;\    &nbsp;\  
          N\               134\         13\        147\    
       Row(%)\            91.2%\       8.8%\      98.0%\   
      Column(%)\          99.3%\       86.7%\        \     
       Total(%)             89.3%        8.7%              

        Total\              135\         15\        150\   
                             90%         10%               
-----------------------------------------------------------

Table: Third Attention Check $\times$ Bot Status

3) Mean sawtooth survey complete time by bot status
```{r}
# aggregate(pilot1[, "md_time_inSec"], list(pilot1$md_fit_cut), mean, na.rm = T)

Mdtime.bot <- pilot1 %>% group_by(md_fit_cut) %>% summarise(mean(md_time_inSec, na.rm = T), N = sum(!is.na(md_time_inSec)))
Mdtime.bot <- Mdtime.bot[-3, ]
colnames(Mdtime.bot) <- c("Bot Status", "Mean", "N")
knitr::kable(Mdtime.bot, digits = 2, caption = "Mean Sawtooth Survey Complete Time (seconds)")

```

4) Mean sawtooth survey complete time by number of attention checks failed
```{r}
# mean(pilot1[pilot1$sum.att.failure == 0, "md_time_inSec"], na.rm = T)
# mean(pilot1[pilot1$sum.att.failure == 1, "md_time_inSec"], na.rm = T)
# mean(pilot1[pilot1$sum.att.failure == 2, "md_time_inSec"], na.rm = T)

# aggregate(pilot1[, "md_time_inSec"], list(pilot1$sum.att.failure), mean, na.rm = T)

Mdtime.sum.fail <- pilot1 %>% group_by(sum.att.failure) %>% summarise(mean(md_time_inSec, na.rm = T), N = sum(!is.na(md_time_inSec)))
colnames(Mdtime.sum.fail) <- c("Number of Attetion Check Failure", "Mean", "Valid N")
knitr::kable(Mdtime.sum.fail, digits = 2, caption = "Mean Sawtooth Survey Complete Time (seconds)")
```

