---
title: "Pilot 2"
author: "Yi"
date: "4/29/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(gmodels)
library(pander)
panderOptions("round", 1)
```

```{r, include=FALSE}
# load the dataset
data <- read.csv('/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04292020/Prolific2.csv', stringsAsFactors = FALSE)
```

```{r}
# explore attention check questions

# result of each attention check question
data <- mutate(data, att1.success = ifelse(data$att_check1___1 == 1 & data$att_check1___4 == 1 & data$att_check1___5 == 1, 1, 0))

data <- mutate(data, att2.success = ifelse(data$last_30_ecig_yn == 1 & data$att_check2 == 3, 1, ifelse(data$last_30_ecig_yn == 1, 0, NA))) # people who are not asked the second question are marked as NA

data <- mutate(data, att3.success = ifelse(data$att_check3a == 4 & grepl("decision making", data$att_check3b, ignore.case = T), 1, 0))

data$att2.replaceNA <- data$att2.success
data$att2.replaceNA[is.na(data$att2.replaceNA)] <- 1 # people who are not asked are marked as success

data$sum.att.success <- apply(data[, c("att1.success", "att2.replaceNA", "att3.success")], 1, sum)

data$sum.att.failure <- 3 - data$sum.att.success

data$att1.success <- factor(data$att1.success, levels = c(0, 1), labels = c("fail", "success"))
data$att2.replaceNA <- factor(data$att2.replaceNA, levels = c(0, 1), labels = c("fail", "success"))
data$att3.success <- factor(data$att3.success, levels = c(0,1), labels = c("fail", "success"))

```

```{r}
Freq <- as.data.frame(matrix(table(data$sum.att.failure)))
Perc <- as.data.frame(matrix(prop.table(table(data$sum.att.failure)) * 100)) 
table.count.failure <- cbind(Freq, Perc)
table.count.failure[5, ] <- c(sum(table.count.failure[, 1]), sum(table.count.failure[, 2]))
rownames(table.count.failure) <- c(0, 1, 2, 3, "Total")
colnames(table.count.failure) <- c("Frequency", "Percentage (%)")

knitr::kable(table.count.failure, digits = 1, caption = "Number of Attention Check Failed")
```

1) A cross tab of number of attention checks failed (0-3) by bot status
```{r, include=FALSE}
bot <- readRDS("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04232020/MaxDiff_Pilot2_BotFit.rds")

count <- select(data, redcapid, sum.att.failure)

pilot2 <- left_join(count, bot, by = "redcapid")

# table(pilot2$sum.att.failure, pilot2$md_fit_cut)
pander:: pander(descr::CrossTable(pilot2$sum.att.failure, pilot2$md_fit_cut, prop.chisq = FALSE, dnn = c("Number of Attention Check Failures", "Bot Status")), caption = "Number of Attention Check Failures X Bot Status", digits = panderOptions("round"))

```

---------------------------------------------------------------
          &nbsp;\            Bot Status\   &nbsp;\    &nbsp;\  
 Number of Attention Check        0           1        Total   
         Failures                                              
--------------------------- ------------- ---------- ----------
          **0**\              &nbsp;\      &nbsp;\    &nbsp;\  
            N\                 237\         17\        254\    
         Row(%)\              93.3%\       6.7%\      84.1%\   
        Column(%)\            85.9%\       65.4%\        \     
         Total(%)               78.5%        5.6%              

          **1**\              &nbsp;\      &nbsp;\    &nbsp;\  
            N\                  38\          8\        46\     
         Row(%)\              82.6%\       17.4%\     15.2%\   
        Column(%)\            13.8%\       30.8%\        \     
         Total(%)               12.6%        2.6%              

          **2**\              &nbsp;\      &nbsp;\    &nbsp;\  
            N\                  1\           1\         2\     
         Row(%)\              50.0%\       50.0%\     0.7%\    
        Column(%)\             0.4%\       3.8%\         \     
         Total(%)               0.3%         0.3%              

          **3**\              &nbsp;\      &nbsp;\    &nbsp;\  
            N\                  0\           0\         0\     
         Row(%)\               NaN%\       NaN%\      0.0%\    
        Column(%)\             0.0%\       0.0%\         \     
         Total(%)               0.0%         0.0%              

          Total\                276\         26\        302\   
                                91.4%        8.6%              
---------------------------------------------------------------

Table: Number of Attention Check Failures $\times$ Bot Status


2) A cross tab of each attention check (failed vs. did not fail) by bot status 
```{r, include=FALSE}
each.failure <- select(data, redcapid, att1.success, att2.replaceNA, att3.success)

pilot2.each <- left_join(each.failure, bot, by = "redcapid")

pander:: pander(descr::CrossTable(pilot2.each$att1.success, pilot2.each$md_fit_cut, prop.chisq = FALSE, dnn = c("First Attention Check", "Bot Status")), caption = "First Attention Check X Bot Status", digits = panderOptions("round"))
```

-----------------------------------------------------------
        &nbsp;\          Bot Status\   &nbsp;\    &nbsp;\  
 First Attention Check        0           1        Total   
----------------------- ------------- ---------- ----------
      **fail**\           &nbsp;\      &nbsp;\    &nbsp;\  
          N\                32\          4\        36\     
       Row(%)\            88.9%\       11.1%\     11.9%\   
      Column(%)\          11.6%\       15.4%\        \     
       Total(%)             10.6%        1.3%              

     **success**\         &nbsp;\      &nbsp;\    &nbsp;\  
          N\               244\         22\        266\    
       Row(%)\            91.7%\       8.3%\      88.1%\   
      Column(%)\          88.4%\       84.6%\        \     
       Total(%)             80.8%        7.3%              

        Total\              276\         26\        302\   
                            91.4%        8.6%              
-----------------------------------------------------------

Table: First Attention Check $\times$ Bot Status

```{r, include=FALSE}
pander:: pander(descr::CrossTable(pilot2.each$att2.replaceNA, pilot2.each$md_fit_cut, prop.chisq = FALSE, dnn = c("Second Attention Check", "Bot Status")), caption = "Second Attention Check X Bot Status", digits = panderOptions("round"))
```

------------------------------------------------------------
        &nbsp;\           Bot Status\   &nbsp;\    &nbsp;\  
 Second Attention Check        0           1        Total   
------------------------ ------------- ---------- ----------
       **fail**\           &nbsp;\      &nbsp;\    &nbsp;\  
          N\                 5\           3\         8\     
        Row(%)\            62.5%\       37.5%\     2.6%\    
      Column(%)\            1.8%\       11.5%\        \     
        Total(%)             1.7%         1.0%              

     **success**\          &nbsp;\      &nbsp;\    &nbsp;\  
          N\                271\         23\        294\    
        Row(%)\            92.2%\       7.8%\      97.4%\   
      Column(%)\           98.2%\       88.5%\        \     
        Total(%)             89.7%        7.6%              

         Total\              276\         26\        302\   
                             91.4%        8.6%              
------------------------------------------------------------

Table: Second Attention Check $\times$ Bot Status

```{r, include=FALSE}
pander:: pander(descr::CrossTable(pilot2.each$att3.success, pilot2.each$md_fit_cut, prop.chisq = FALSE, dnn = c("Third Attention Check", "Bot Status")), caption = "Third Attention Check X Bot Status", digits = panderOptions("round"))
```

-----------------------------------------------------------
        &nbsp;\          Bot Status\   &nbsp;\    &nbsp;\  
 Third Attention Check        0           1        Total   
----------------------- ------------- ---------- ----------
      **fail**\           &nbsp;\      &nbsp;\    &nbsp;\  
          N\                3\           3\         6\     
       Row(%)\            50.0%\       50.0%\     2.0%\    
      Column(%)\           1.1%\       11.5%\        \     
       Total(%)             1.0%         1.0%              

     **success**\         &nbsp;\      &nbsp;\    &nbsp;\  
          N\               273\         23\        296\    
       Row(%)\            92.2%\       7.8%\      98.0%\   
      Column(%)\          98.9%\       88.5%\        \     
       Total(%)             90.4%        7.6%              

        Total\              276\         26\        302\   
                            91.4%        8.6%              
-----------------------------------------------------------

Table: Third Attention Check $\times$ Bot Status

3) Mean sawtooth survey complete time by bot status
```{r}
Mdtime.bot <- pilot2 %>% group_by(md_fit_cut) %>% summarise(mean(md_time_inSec, na.rm = T), N = sum(!is.na(md_time_inSec)))

Mdtime.bot <- Mdtime.bot[-3, ]
colnames(Mdtime.bot) <- c("Bot Status", "Mean", "N")

knitr::kable(Mdtime.bot, digits = 2, caption = "Mean Sawtooth Survey Complete Time (seconds)")
```

4) Mean sawtooth survey complete time by number of attention checks failed
```{r}
Mdtime.sum.fail <- pilot2 %>% group_by(sum.att.failure) %>% summarise(mean(md_time_inSec, na.rm = T), N = sum(!is.na(md_time_inSec)))

colnames(Mdtime.sum.fail) <- c("Number of Attetion Check Failure", "Mean", "Valid N")
knitr::kable(Mdtime.sum.fail, digits = 2, caption = "Mean Sawtooth Survey Complete Time (seconds)")

```

5) Mean redcap survey complete time by bot status
```{r}
time.ncol <- ends_with("timestamp", vars = colnames(data))
start <- time.ncol[1]
end <- time.ncol[length(time.ncol)]

data$start.time <- strptime(data[, start], format = "%Y-%m-%d %H:%M:%S") 
data$end.time <- strptime(data[, end], format = "%Y-%m-%d %H:%M:%S")

data$diff.time <- difftime(data$end.time, data$start.time, units = "secs")
data$diff.time <- as.numeric(data$diff.time)

RCtime <- select(data, redcapid, diff.time)

RCtime.bot.data <- left_join(RCtime, bot, by = "redcapid")
```

```{r}
RCtime.bot <- RCtime.bot.data %>% group_by(md_fit_cut) %>% summarise(mean(diff.time, na.rm = T), N = sum(!is.na(diff.time)))

colnames(RCtime.bot) <- c("Bot Status", "Mean", "N")

knitr::kable(RCtime.bot, digits = 2, caption = "Mean Redcap Survey Complete Time (seconds)")
```

6) Mean redcap survey complete time by number of attention checks failed
```{r}
RCtime.att.data <- select(data, redcapid, diff.time, sum.att.failure)

RCtime.sum.fail <- RCtime.att.data %>% group_by(sum.att.failure) %>% summarise(mean(diff.time, na.rm = T), N = sum(!is.na(diff.time)))

colnames(RCtime.sum.fail) <- c("Number of Attetion Check Failure", "Mean", "Valid N")
knitr::kable(RCtime.sum.fail, digits = 2, caption = "Mean Redcap Survey Complete Time (seconds)")
```

