---
title: "Pilot1"
author: "Yi"
date: "4/23/2020"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(gmodels)
library(pander)
```

```{r, include=FALSE}
# load the dataset
data <- read.csv('/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04232020/ConjointAnalysisProl_DATA_2020-04-23_1502.csv')
```

```{r}
# explore attention check questions

 # table(data$att_check1___1, useNA = "always")
 # table(data$att_check1___2, useNA = "always")
 # table(data$att_check1___3, useNA = "always")
 # table(data$att_check1___4, useNA = "always")
 # table(data$att_check1___5, useNA = "always")
 # table(data$att_check2, useNA = "always")
 # table(data$last_30_ecig_yn, useNA = "always")

 # table(data$att_check3a, useNA = "always")
 # table(data$att_check3b, useNA = "always")

# result of each attention check question
data <- mutate(data, att1.success = ifelse(data$att_check1___1 == 1 & data$att_check1___4 == 1 & data$att_check1___5 == 1, 1, 0))

data <- mutate(data, att2.success = ifelse(data$last_30_ecig_yn == 1 & data$att_check2 == 3, 1, ifelse(data$last_30_ecig_yn == 1, 0, NA))) # people who are not asked the second question are marked as NA

data <- mutate(data, att3.success = ifelse(data$att_check3a == 4 & grepl("decision making", data$att_check3b, ignore.case = T), 1, 0))

# table(data$att2.success, useNA = "always")
data$att2.replaceNA <- data$att2.success
data$att2.replaceNA[is.na(data$att2.replaceNA)] <- 1 # people who are not asked are marked as success
# table(data$att2.replaceNA, useNA = "always")

data$sum.att.success <- apply(data[, c("att1.success", "att2.replaceNA", "att3.success")], 1, sum)

data$sum.att.failure <- 3 - data$sum.att.success

data$att1.success <- factor(data$att1.success, levels = c(0, 1), labels = c("fail", "success"))
data$att2.replaceNA <- factor(data$att2.replaceNA, levels = c(0, 1), labels = c("fail", "success"))
data$att3.success <- factor(data$att3.success, levels = c(0,1), labels = c("fail", "success"))
```

```{r}
Freq <- as.data.frame(matrix(table(data$sum.att.failure)))
Perc <- as.data.frame(matrix(prop.table(table(data$sum.att.failure)) * 100)) 
table.count.failure <- cbind(Freq, Perc)
table.count.failure <- rbind(table.count.failure, c(0, 0))
rownames(table.count.failure) <- c(0, 1, 2, 3)
colnames(table.count.failure) <- c("Frequency", "Percentage (%)")

knitr::kable(table.count.failure, digits = 1, caption = "Number of Attention Check Failed")
```

1) A cross tab of number of attention checks failed (0-3) by bot status

```{r, include=FALSE}

bot <- readRDS("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/04232020/MaxDiff_Pilot1_BotFit.rds")

count <- select(data, redcapid, sum.att.failure)

pilot1 <- left_join(count, bot, by = "redcapid")

xtabs(~ sum.att.failure + md_fit_cut, data = pilot1)

pander:: pander(CrossTable(pilot1$sum.att.failure, pilot1$md_fit_cut, prop.chisq = FALSE), caption = "table 2")

```

--------------------------------------------------------------------------
        &nbsp;\              bot status\          &nbsp;\        &nbsp;\   
 number of attention\              &nbsp;\            \             \ 
 check failed                       0                 1            Total    
------------------------ -------------------- -------------- -------------
        **0**\                 &nbsp;\           &nbsp;\       &nbsp;\    
          N\                    113\              12\           125\      
        Row(%)\              90.4000%\          9.6000%\      83.3333%\   
      Column(%)\             83.7037%\         80.0000%\           \      
        Total(%)               75.3333%          8.0000%                  

        **1**\                 &nbsp;\           &nbsp;\       &nbsp;\    
          N\                    22\                2\            24\      
        Row(%)\              91.6667%\          8.3333%\      16.0000%\   
      Column(%)\             16.2963%\         13.3333%\           \      
        Total(%)               14.6667%          1.3333%                  

        **2**\                 &nbsp;\           &nbsp;\       &nbsp;\    
          N\                     0\                1\            1\       
        Row(%)\               0.0000%\         100.0000%\     0.6667%\    
      Column(%)\              0.0000%\          6.6667%\           \      
        Total(%)               0.0000%           0.6667%                  

         Total\                 135\               15\           150\     
                                 90%               10%                    
--------------------------------------------------------------------------

Table: Number of Attention Check Failures X Bot Status

2) A cross tab of each attention check (failed vs. did not fail) by bot status 
```{r, include=FALSE}
each.failure <- select(data, redcapid, att1.success, att2.replaceNA, att3.success)

pilot1.each <- left_join(each.failure, bot, by = "redcapid")

pander:: pander(CrossTable(pilot1.each$att1.success, pilot1.each$md_fit_cut, prop.chisq = FALSE), caption = "First Attention Check X Bot Status")
```

--------------------------------------------------------------------------------
         &nbsp;\                   Bot Status\          &nbsp;\       &nbsp;\   
 First Attention Check                0                   1           Total    
-------------------------- ------------------------- ------------- -------------
        **fail**\                  &nbsp;\             &nbsp;\       &nbsp;\    
           N\                        19\                 2\            21\      
         Row(%)\                  90.4762%\           9.5238%\      14.0000%\   
       Column(%)\                 14.0741%\           13.3333%\          \      
         Total(%)                  12.6667%             1.3333%                 

      **success**\                 &nbsp;\             &nbsp;\       &nbsp;\    
           N\                       116\                 13\          129\      
         Row(%)\                  89.9225%\           10.0775%\     86.0000%\   
       Column(%)\                 85.9259%\           86.6667%\          \      
         Total(%)                  77.3333%             8.6667%                 

          Total\                     135\                15\           150\     
                                      90%                 10%                   
--------------------------------------------------------------------------------

Table: First Attention Check X Bot Status

```{r, include=FALSE}
pander:: pander(CrossTable(pilot1.each$att2.replaceNA, pilot1.each$md_fit_cut, prop.chisq = FALSE), caption = "Second Attention Check X Bot Status")
```

--------------------------------------------------------------------------------
          &nbsp;\             pilot1.each$md_fit_cut\     &nbsp;\       &nbsp;\   
 Second Attention Check             0                   1              Total
-------------------------- ------------------------- ------------- -------------
         **fail**\                   &nbsp;\              &nbsp;\      &nbsp;\  
            N\                         2\                   0\          2\ 
          Row(%)\                  100.0000%\            0.0000%\     1.3333%\ 
        Column(%)\                  1.4815%\             0.0000%\        \
          Total(%)                    1.3333%             0.0000%    

       **success**\                  &nbsp;\              &nbsp;\     &nbsp;\
            N\                        133\                 15\         148\
          Row(%)\                   89.8649%\           10.1351%\     98.6667%\ 
        Column(%)\                  98.5185%\           100.0000%\       \
          Total(%)                   88.6667%             10.0000%   

           Total\                      135\                 15\          150\ 
                                        90%                 10%      
---------------------------------------------------------------------

Table: Second Attention Check X Bot Status 

```{r, include=FALSE}
pander:: pander(CrossTable(pilot1.each$att3.success, pilot1.each$md_fit_cut, prop.chisq = FALSE), caption = "Third Attention Check X Bot Status")
```
 
--------------------------------------------------------------------------------
         &nbsp;\                   Bot Status\          &nbsp;\       &nbsp;\   
Third Attention Check                 0                   1           Total    
-------------------------- ------------------------- ------------- -------------
        **fail**\                  &nbsp;\             &nbsp;\       &nbsp;\    
           N\                        1\                  2\            3\       
         Row(%)\                  33.3333%\           66.6667%\     2.0000%\    
       Column(%)\                 0.7407%\            13.3333%\          \      
         Total(%)                   0.6667%             1.3333%                 

      **success**\                 &nbsp;\             &nbsp;\       &nbsp;\    
           N\                       134\                 13\          147\      
         Row(%)\                  91.1565%\           8.8435%\      98.0000%\   
       Column(%)\                 99.2593%\           86.6667%\          \      
         Total(%)                  89.3333%             8.6667%                 

          Total\                     135\                15\           150\     
                                      90%                 10%                   
--------------------------------------------------------------------------------

Table: Third Attention Check X Bot Status

3) Mean sawtooth survey complete time by bot status
```{r}
# aggregate(pilot1[, "md_time_inSec"], list(pilot1$md_fit_cut), mean, na.rm = T)

Mdtime.bot <- pilot1 %>% group_by(md_fit_cut) %>% summarise(mean(md_time_inSec, na.rm = T), N = sum(!is.na(md_time_inSec)))
Mdtime.bot <- Mdtime.bot[-3, ]
colnames(Mdtime.bot) <- c("Bot Status", "Mean", "N")
knitr::kable(Mdtime.bot, digits = 2, caption = "Sawtooth Survey Complete Time (seconds) X Bot Status")

```

4) Mean sawtooth survey complete time by number of attention checks failed
```{r}
# mean(pilot1[pilot1$sum.att.failure == 0, "md_time_inSec"], na.rm = T)
# mean(pilot1[pilot1$sum.att.failure == 1, "md_time_inSec"], na.rm = T)
# mean(pilot1[pilot1$sum.att.failure == 2, "md_time_inSec"], na.rm = T)

# aggregate(pilot1[, "md_time_inSec"], list(pilot1$sum.att.failure), mean, na.rm = T)

Mdtime.sum.fail <- pilot1 %>% group_by(sum.att.failure) %>% summarise(mean(md_time_inSec, na.rm = T), N = sum(!is.na(md_time_inSec)))
colnames(Mdtime.sum.fail) <- c("Number of Attetion Check Failure", "Mean", "Valid N")
knitr::kable(Mdtime.sum.fail, digits = 2, caption = "Sawtooth Survey Complete Time (seconds) X Number of Attention Check Failure")
```

