---
title: "merge and analyze prolific 2 & 3 (complete)"
author: "Yi"
date: "7/15/2020"
output:
  html_document:
    df_print: paged
---
<style type="text/css">
body{ /* Normal  */
      font-size: 16px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r load packages, include=FALSE}
library(tidyverse)
library(gdata)
library(descr)
library(Hmisc)
library(expss)
library(kableExtra)
```

```{r read datasets}
data1 <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/07122020/Prolific Pilot3_minus.csv", na.strings = "", stringsAsFactors = F)

data2 <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/07122020/Prolific Pilot3_second.csv", na.strings = "", stringsAsFactors = F)

prolific2 <- read.csv('/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/07122020/Prolific Pilot2.csv', na.strings = "", stringsAsFactors = F)

idlist <- read.xls("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/Pilot 3 Eligible.xlsx")

maxdiff_pilot3 <- read.csv("/Users/zhan039/Desktop/USC_HEAL/EVOC (CONJOINT)/MaxDiff_eCigs_ProlificV3_data.csv", na.strings = "", stringsAsFactors = F)

```

## 1. Data Cleaning
```{r check and clean prolific 3, include=FALSE}
length(unique(data1$prolificpid)) # 4 repeated records
length(unique(data2$prolificpid)) # 1 repeated records

# clean data1
data1$num.na <- rowSums(is.na(data1))
data1 %>% group_by(prolificpid) %>% summarise(., n = n()) %>% filter(., n > 1)

data1[data1$prolificpid == "5a2add709408dc00016f57d3", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 1084
data1[data1$prolificpid == "5cc210247502a000125f9886", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 1134
data1[data1$prolificpid == "5ce649e53e496100197ae3db", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 1053
data1[data1$prolificpid == "5d219d16072b440018aebe98", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 1023

data1[data1$prolificpid == "test", ]  # remove redcapid = 1000

data1 <- data1[!data1$redcapid %in% c(1084, 1134, 1053, 1023, 1000), ] 

x1 <- merge(data1, maxdiff_pilot3[, c("prolificpid", "sys_RespStatus")], all.x = T, by = "prolificpid")
sum(data1$prolificpid %in% x1$prolificpid)
x1$num.na.new <- rowSums(is.na(x1))
x1 %>% group_by(prolificpid) %>% summarise(., n = n()) %>% filter(., n > 1)
x1[x1$prolificpid == "5cc210247502a000125f9886", c("redcapid", "prolificpid", "num.na.new", "sys_RespStatus")]
x1 <- x1[-c(77, 78),]
dim(x1[x1$sys_RespStatus %in% 5, ])
x1[!x1$sys_RespStatus %in% 5, ]
x1 <- x1[x1$sys_RespStatus %in% 5, ]

# clean data2
data2$num.na <- rowSums(is.na(data2))
data2 %>% group_by(prolificpid) %>% summarise(., n = n()) %>% filter(., n > 1)

data2[data2$prolificpid == "5da2d3e256940100160c3bec", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 2039  # filter(data2[, c("redcapid", "prolificpid", "num.na")], prolificpid == "5da2d3e256940100160c3bec") cannot detect NA

data2[is.na(data2$prolificpid), c("redcapid", "prolificpid", "num.na")] # remove redcapid = 2000

data2[data2$prolificpid == "5c5002c6ee5ae100010a2f3b", ] # remove redcapid = 2063

data2 <- data2[!data2$redcapid %in% c(2000, 2039, 2063), ]

x2 <- merge(data2, maxdiff_pilot3[, c("prolificpid", "sys_RespStatus")], all.x = T, by = "prolificpid")
sum(data2$prolificpid %in% x2$prolificpid)
x2$num.na.new <- rowSums(is.na(x2))
x2 %>% group_by(prolificpid) %>% summarise(., n = n()) %>% filter(., n > 1)
x2[x2$prolificpid == "5a1303419b760100013a7dd9", c("redcapid", "prolificpid", "num.na.new", "sys_RespStatus")]
x2[x2$prolificpid == "5da2d3e256940100160c3bec", c("redcapid", "prolificpid", "num.na.new", "sys_RespStatus")]
x2 <- x2[-c(4, 45),]
dim(x2[x2$sys_RespStatus %in% 5, ])
x2[is.na(x2$sys_RespStatus), c("redcapid", "prolificpid", "sys_RespStatus")]
x2[!x2$sys_RespStatus %in% 5, c("redcapid", "prolificpid", "sys_RespStatus")]
x2 <- x2[x2$sys_RespStatus %in% 5, ] 

data1 <- x1
data2 <- x2
```
### Prolific Pilot 3 (minus illicit drugs and cannabis)
N = 167 (Raw data)
<br>Repeated ids: "5a2add709408dc00016f57d3", "5cc210247502a000125f9886", "5ce649e53e496100197ae3db", "5d219d16072b440018aebe98"
<br>Invalid id: “test”
<br>N = 162 (Cleaned data) (deleted redcapid: 1084, 1134, 1053, 1023, 1000)
<br>N = 154 (Cleaned data with completeness information from Maxdiff data) (deleted redcapid: 1059, 1112, 1125, 1078, 1014, 1041, 1063, 1166)

### Prolific Pilot 3 (second wave data collection)
N = 65 (Raw data)
<br>Repeated ids: “5da2d3e256940100160c3bec”
<br>Invalid id: missing value, “5c5002c6ee5ae100010a2f3b” (This id is not included in the ID list)
<br>N = 62 (Cleaned data) (deleted redcapid: 2000, 2039， 2063)
<br>N = 61 (Cleaned data with completeness information from Maxdiff data) (deleted redcapid: 2049)
```{r merge prolific 3, include=FALSE}
# merge prolific 3
length(unique(data1$prolificpid))
length(unique(data2$prolificpid))

intersec_name_3 <- intersect(colnames(data1), colnames(data2))
colnames(data1)[!colnames(data1) %in% intersec_name_3]
colnames(data2)[!colnames(data2) %in% intersec_name_3]
length(intersect(data1$prolificpid, data2$prolificpid))

309+ 2 + 16  # 327 columns

prolific3 <- merge(data1, data2, all.x = T, all.y = T)

length(intersect(colnames(data1), colnames(prolific3)))
length(intersect(colnames(data2), colnames(prolific3)))
# full_join(data1, data2, by = intersect(colnames(data1), colnames(data2)))

sum(prolific3$prolificpid %in% idlist$Pilot3Eligible)  # "test" is not in the id list; "5c5002c6ee5ae100010a2f3b" is not in the id list
prolific3[!prolific3$prolificpid %in% idlist$Pilot3Eligible, "redcapid"]

prolific3 <- prolific3[prolific3$prolificpid %in% idlist$Pilot3Eligible, ] # remove "test" and "5c5002c6ee5ae100010a2f3b"

```

```{r check and clean prolific 2, include=FALSE}
length(unique(prolific2$prolificpid)) # 9 repeated records

prolific2$num.na <- rowSums(is.na(prolific2))

prolific2 %>% group_by(prolificpid) %>% summarise(n = n()) %>% filter( n > 1)

prolific2[prolific2$prolificpid == "5c315f577626080001a88cb2", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 8109

prolific2[prolific2$prolificpid == "5c748b9188fdc20017c60436", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 8272

prolific2[prolific2$prolificpid == "5d010ccecfeb82000117c42a", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 8241 8244	

prolific2[prolific2$prolificpid == "5d30b94628b06900195d305e", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 8088		

prolific2[prolific2$prolificpid == "5d6f02d4e0207600167e2317", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 8158	8168

prolific2[prolific2$prolificpid == "5dac7c198ff76d00166a70c4", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 8040

prolific2[prolific2$prolificpid == "5df1683537241c07cf8f3984", c("redcapid", "prolificpid", "num.na")]  # remove redcapid = 8160

prolific2 <- prolific2[!prolific2$redcapid %in% c(8109, 8272, 8241, 8244, 8088, 8158,	8168, 8040, 8160), ]

intersec_name_2_3 <- intersect(colnames(prolific2), colnames(prolific3))

colnames(prolific2)[!colnames(prolific2) %in% intersec_name_2_3]
colnames(prolific3)[!colnames(prolific3) %in% intersec_name_2_3]

length(intersect(prolific2$prolificpid, prolific3$prolificpid))

sum(is.na(prolific2$prolificpid))

184 + 49 + 143 # 376 columns
```
### Prolific Pilot 2
N = 332 (Raw Data)
<br>Repeated ids: “5c315f577626080001a88cb2”, “5c748b9188fdc20017c60436”, “5d010ccecfeb82000117c42a”, “5d30b94628b06900195d305e”, “5d6f02d4e0207600167e2317”, “5dac7c198ff76d00166a70c4”, “5df1683537241c07cf8f3984”
<br>N = 323 (Cleaned Data) (deleted redcapid: 8109, 8272, 8241, 8244, 8088, 8158,	8168, 8040, 8160)
```{r merge prolifc 2 & 3, include=FALSE}
prolific2$pilot <- 2
prolific3$pilot <- 3
intersec_name_2_3 <- intersect(colnames(prolific2), colnames(prolific3))

185 + 49 + 143 # 377 columns

prolific_2_3 <- merge(prolific2, prolific3, all.x = T, all.y = T, by = c("prolificpid", "pilot", intersec_name_2_3[!intersec_name_2_3 %in% c("prolificpid", "pilot")]))
```
### Merged Dataset (long format)
N = 538
<br>215 participants get enrolled in both pilot 2 and 3.

## 2. Data Analysis (N = 430, # of participants = 215)

```{r labels}
# LABELS
# pilot
val_lab(prolific_2_3$pilot) <- num_lab("
                                    2 Pilot 2
                                    3 Pilot 3
                                    ")

# Frequency of number of days of use
varlist_num_days <- colnames(prolific_2_3)[endsWith(colnames(prolific_2_3), "30_days")]

for(i in 1:length(varlist_num_days)){
  
  varname = varlist_num_days[i]
  prolific_2_3[, varname] <- factor(prolific_2_3[, varname], levels = c(1:7), labels = c("0 days", "1 or 2 days", "3 to 5 days", "6 to 9 days", "10 to 19 days", "20 to 29 days", "All 30 days"))
  
}

# every_day_current
prolific_2_3$vape_every_day_current <- factor(prolific_2_3$vape_every_day_current, levels = c(0:1), labels = c("no", "Yes"))

# ecig_bout
prolific_2_3$ecig_bout_times_last30 <- factor(prolific_2_3$ecig_bout_times_last30, levels = c(1:7), labels = c("1 time per day", "2 times per day", "3 to 5 times per day", "6 to 9 times per day", "10 to 14 times per day", "15 to 20 times per day", "More than 20 times per day"))

# ecig_bout_puffs_last30
prolific_2_3$ecig_bout_puffs_last30 <- factor(prolific_2_3$ecig_bout_puffs_last30, levels = c(1:7), labels = c("1 puff", "2 puffs", "3 to 5 puffs", "6 to 9 puffs", "10 to 14 puffs", "15 to 20 puffs", "More than 20 puffs"))

# myecig_type
prolific_2_3$myecig_type <- factor(prolific_2_3$myecig_type, levels = c(1:7), labels = c("Juul or similar style device", "Suorin or similar device", "Puffbar or similar device", "Box mod", "Squonk mod", "Vape pen", "Other (please specify)"))
```

```{r functions}
# FUNCTIONS
Days_Pilot <- function(varname){
  
  temp.table <- table(validdata[, varname], validdata$pilot, useNA = "ifany")
  rowname <- dimnames(temp.table)[[1]]
  rowname[is.na(rowname)] <- "Missing Value"
  dimnames(temp.table)[[1]] <- rowname
  
kableExtra::kable(temp.table, format = "html", caption = varname) %>% kable_styling(bootstrap_options = "striped", full_width = F)
  
}

FreqPerct <- function(varname){
  freq <- table(validdata[, varname], validdata$pilot, useNA = "ifany")
  rowname <- dimnames(freq)[[1]]
  rowname[is.na(rowname)] <- "Missing Value"
  dimnames(freq)[[1]] <- rowname
  
  perct <- round(prop.table(freq, margin = 2) * 100, 1)
  nperct <- paste(freq, " ", "(", perct, "%", ")", sep = "")
  table <- matrix(nperct, ncol = ncol(freq))
  colnames(table) <- colnames(freq)
  rownames(table) <- rownames(freq)
  kableExtra::kable(table, format = "html", caption = varname) %>% kable_styling(bootstrap_options = "striped", full_width = F)
}

```

### Frequency of number of days of use for each device type in pilot 2 vs. pilot 3
```{r Frequency of number of days of use, results = "asis"}
# analytical dataset
validdata <- prolific_2_3[prolific_2_3$prolificpid %in% prolific3$prolificpid, ]  # get enrolled in both pilot 2 and 3

varlist_num_days <- colnames(prolific_2_3)[endsWith(colnames(prolific_2_3), "30_days")]

lapply(varlist_num_days, Days_Pilot)
```

### N(%) of "every_day_current" in pilot 2 vs. pilot 3
```{r every_day_current}
# Days_Pilot("vape_every_day_current")
# prop.table(table(validdata$vape_every_day_current, validdata$pilot, useNA = "always"))
FreqPerct("vape_every_day_current")
```


### N(%) of ecig_bout in pilot 2 vs. pilot
```{r ecig_bout}
# Days_Pilot("ecig_bout_times_last30")
# prop.table(table(validdata$ecig_bout_times_last30, validdata$pilot, useNA = "always"))
FreqPerct("ecig_bout_times_last30")

# Days_Pilot("ecig_bout_puffs_last30")
# prop.table(table(validdata$ecig_bout_puffs_last30, validdata$pilot, useNA = "always"))
FreqPerct("ecig_bout_puffs_last30")

```

### N(%) of dependence based on any 'yes' responses to questions in either the "vape addiction" or "vape quit effects" matrices 
```{r dependence based on vape addicion or vape quit effects, include=FALSE}
select(validdata, starts_with(c("vape_addiction", "vape_quit_effects")))
table(rowSums(is.na(select(validdata, starts_with(c("vape_addiction", "vape_quit_effects")))
)))  # 8 participants have missing value for all items

validdata$dependence.na <- rowSums(is.na(select(validdata, starts_with(c("vape_addiction", "vape_quit_effects")))))
validdata$dependence.vape <- rowSums(select(validdata, starts_with(c("vape_addiction", "vape_quit_effects"))))  # no need to remove na because number of na is 0 or 10
validdata <- mutate(validdata, dependence.vape.d = ifelse(dependence.vape > 0, 1, 0))

validdata$dependence.vape.d <- factor(validdata$dependence.vape.d, levels = c(0, 1), labels = c("No", "Yes"))

table(validdata$dependence.na, useNA = "always")
table(validdata$dependence.vape, useNA = "always")
table(validdata$dependence.vape.d, useNA = "always")

select(validdata, prolificpid,starts_with(c("vape_addiction", "vape_quit_effects")), dependence.na, dependence.vape, dependence.vape.d)

Days_Pilot("dependence.vape.d")
prop.table(table(validdata$dependence.vape.d, validdata$pilot))
```

```{r}
FreqPerct("dependence.vape.d")
```

### N(%) for each category of type of device used (var "myecig_type")
```{r myecig_type}
# Days_Pilot("myecig_type")
# prop.table(table(validdata$myecig_type, validdata$pilot), margin = 2)
FreqPerct("myecig_type")
```


### Frequencies for all of the COVID questions from var covid_63 to covid_89h
```{r covid_63 to covid_89h, include=FALSE}
colnames(validdata)[startsWith(colnames(validdata), "covid")][-c(1:10, 79, 80)]

covidvars <- colnames(validdata)[startsWith(colnames(validdata), "covid")][-c(1:10, 79, 80)]

FreqTable <- function(varvec){
  
  temp.table <- table(varvec, useNA = "always")

  report <- list()
  report[[1]] <- names(varvec)
  report[[2]] <- temp.table

  return(report)
  
}

apply(validdata[, covidvars], 2, FreqTable)
```

```{r, results="asis"}
CovidFun <- function(varname){
  covidtab <- table(validdata[, varname], useNA = "ifany")
  kableExtra::kable(covidtab, col.names = c(varname, "Frequency")) %>% kable_styling(bootstrap_options = "striped", full_width = F)
}

lapply(covidvars, CovidFun)
```

